% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{book}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{5}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{booktabs}

\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Conflict},
  pdfauthor={Saviour Elikplim Animdife},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Conflict}
\author{Saviour Elikplim Animdife}
\date{April 2025}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{1}
\tableofcontents
}
\chapter*{Preface}\label{preface}
\addcontentsline{toc}{chapter}{Preface}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\textbf{\emph{Conflict}} is my first epic poem. I chanced upon an epic poem somewhere online and remembered John Bunyan's \textbf{\emph{Paradise Lost}}. So, I told myself, ``Why don't you write your first epic poem?'' Well, here it is! It is rather religious but unconventional and even thought-provoking.

I hope this ``longer-than-usual'' poem makes for an enjoyable and intellectually stimulating read and even a jewel for a find. Cheers!

\href{https://github.com/sneurocode/conflict/blob/master/docs/_main.pdf}{Download the PDF version}

© 2025 \emph{Saviour E. Animdife}

\chapter{Lies}\label{lies}

Curse Baalzebub, says my soul;\\
Curse Bel the liar, says my soul.\\
Curse Beelzebub, the prince of demons;\\
Curse Asherah, the Egyptian Ra\\
Of the Samael family.

There are four chiefs of lies;\\
They all go to hell\\
And the Christian one too.\\
There are four princes of lies\\
And they all roast in sorrow.

Tophet is ordained of old;\\
For the king it is prepared\\
And it burns bright and beautifully;\\
It burns with much zeal and splendour.

When Hermes came back from the dead\\
Like Osiris of Egypt,\\
He realized that there was no hell,\\
That the dead are truly dead.\\
It was then that he lost his fear\\
And became Satan's master.\\
His end was worse than his beginning.

Bring forth Nimrod.\\
Does Satan seek to rule hell?\\
Art thou the prince of darkness?\\
Do you rule over souls\\
And decide their fates?

Bring forth Nimrod.\\
Nimrod is a blasphemer\\
And a deceiver.\\
He is the chief,\\
Even the father of lies\\
And Hermes is his son.

Nimrod curses in hell.\\
He sent his angel\\
And Bunyan paid him a visit.\\
Bunyan saw him in his discourse.\\
Nimrod, will thou curse Thunder?\\
Thunder like him if thou art mighty.

Nimrod is with Nimueh.\\
Satan is with Asherah.\\
Dagon is with Baalzebub.\\
They make ready to raise up Hermes.

The two princes of lies\\
Are also the two princes of wickedness;\\
They are Rasha and Resha;\\
They are Bel and Nebo;\\
They are Asherah and Satan;\\
They are the queen and the king of heaven.

The four princes of wickedness,\\
Even the four princes of iniquity\\
Are Baalzebub, Satan, Ninurta and Marduk\\
In that order from most wicked to least.\\
Ninurta is Sin {[}h{]}, Sin of heaven.

Aphrodite, Hermes and Shadel\\
Are the 5th, 6th and 7th princes\\
Of wickedness and iniquity.

Hermes is the sixth\\
And the faller who despises grace and love.\\
He hates chesed with bitterness\\
And God shall make his days most bitter.

Tell me, is Satan the Lord of hell?\\
Does he rule with pachad and terror?\\
Does he take souls and beat them to pulp?\\
Can he bring forth flames\\
That may devour persons\\
As they did to the servants of Job\\
And to his sheep?

Is Satan as mighty,\\
Even as mighty and crazy\\
As the false prophet,\\
As the rock of foolishness,\\
Even as the rebel with Shadel\\
And the antichrist?

Can Satan call down fire like Elijah?\\
Can he repeat his deeds of old?\\
How old is he to start with?\\
Is he as old as An?\\
Can Baalzebub call herself On\\
And not be humiliated in the time to come?

Curse the angel of Satan, says my soul.\\
Curse the princess of darkness;\\
Curse Bel the abominable and vile.\\
Curse the daughter of Babylon,\\
Even the vile daughter of Babylon\\
And the choice daughter of the Assyrian.

There are four chiefs of lies;\\
They all roast in the lake of fire,\\
In that wide and deep abyss of magma\\
Where worms, the voracious maggots,\\
Feast incessantly on their bodies\\
And make clean work of their devil forms.

There are four chiefs of lies;\\
They form the corners\\
And sides and angles of the square.\\
Baal draws it with his detestable finger.

There are four chiefs of lies.\\
They are Satan, Baalzebub,\\
Aphrodite and Hermes.\\
Trust me, these are the ones;\\
These are the ones that roast in the fire.

Satan is the opposite of love\\
And Baalzebub is the opposite of life.\\
Satan is hell\\
And Baalzebub is the bringer of death;\\
Both bring pain and suffering.

Satan is the deceiver, the chief,\\
Baalzebub is the antichrist,\\
The angel of Satan and the enemy,\\
The enemy of all things righteous,\\
Aphrodite is the curse\\
And Hermes is the traitor\\
And the lover and hater of our women.

Aphrodite is a fool;\\
I'm watching for her destruction.\\
What is she? What will she be?\\
She will the mother of torments,

The one who stands by Satan's side\\
In the great and final war\\
And dies, wings broken, by his side\\
Crying, save me, kill him, kill him\\
Though her words be not heard.

So Aphrodite shall die a fool;\\
Baalzebub shall strike the heart of the duck.\\
The cold chicken dies.\\
Aphrodite was a cow, even a coward;\\
She was a golden calf in the desert.

She drew our hearts to her;\\
I despised her; I hated her.\\
She was the angel, the devil\\
That stood for Satan\\
To watch and to stand guard\\
Over Veredel, the leech.\\
She is herself a leech.

She loved herself.\\
Aphrodite is a fool\\
Who hated herself\\
And attacked me\\
And gave counsel to the devil.

She is the bul of Jahbulon.\\
The Media between Satan and Baalzebub.\\
She is the glue or divider between Dagon and Asherah.\\
She is the curse between the Moon and the Sun,\\
Between Amun and Ra.

Cupid said he didn't want me to die.\\
I heard Eros pleading the blood of Jesus.\\
Cupid calls himself a cherub.\\
He makes himself a chubby baby.\\
He says, I'm covenanted with snow.

Aphrodite stood by his table;\\
It was a surgical table.\\
Maybe, they were wont to pry his wings off\\
And kill young Hermes with hypothermia.

Cupid said he loved me.\\
The fool vexed me to death\\
And trusted in Satan his strength\\
And walked with Aphrodite of Venus.\\
Aphrodite, art thou the bright star.\\
Who is Psyche?

Aphrodite competes with Asherah.\\
She wants to be the happy one of Satan,\\
The one who delights in Satan her king\\
Like Elaine never could\\
Because Satan gave her Hermes instead\\
And pleased himself in the vileness.

Aprodite says at the gathering,\\
Let's strike hard.\\
345, let's strike\\
That An may be glorified,\\
That Satan may cease to be Sat-An\\
And rise to become the An.

Aphrodite is a fool.\\
She wields a great sword like the antichrist,\\
Even like Heilel.\\
I said, Aphrodite is a fool.\\
She wants to make herself Satan\\
According to the philosophy of Baalzebub\\
Who says, I am and there is none else.

So, whose advice prevailed\\
Like Qerenel whom the Ultimate\\
Declared infallible?\\
Who prospered like Ashshur the dragon?\\
Was it not Aphrodite, the fool,\\
Unto whom all the demons gave heed?

She sits on the left hand of Satan\\
Waiting to be transferred to his right hand\\
When she deposes Baalzebub the Great\\
Who will then in shame of face\\
Walk over to take the throne of goats\\
While Aphrodite becomes the new sheep.

My soul loathes Aphrodite.\\
She it was who had Sin right where it pleased her\\
And Hermes was shaking his head\\
And saying, Come now, come here,\\
Baalzebub is not called Bel for no reason.

Aphrodite, art thou a black cat\\
Or some black feline?\\
Your skin is all scratched out\\
And your hair is shaggy.

You are bent on having Sin and Satan.\\
Then, the bat flies in the night sky;\\
It is Baalzebub; it is Ishtar\\
And Aphrodite flees from Nanna.

With the mouth shut,\\
She wipes her teeth\\
And says quietly in her soul,\\
I am a good girl, I have done no wrong.

Aphrodite is a witch;\\
She is a sorceress like Baalzebub.

See Aphrodite ready to kill.\\
She is ready to drink blood\\
And to see Satanism prosper.\\
Thou Psyche, Will you\\
Disturb the stillness of my mind\\
And feign innocency like the accursed Veredel?

Foolish Greeks,\\
Your mother, Aphrodite, sends her greetings.\\
She is the devil's scribe and counsellor\\
And the brain behind my affliction.\\
She masterminded the bringing forth,\\
Even the bringing forth of Satanism into public.

She wanted to bring Satan to light\\
So she would be the true Lucy\\
That Bel won't be.\\
She wanted to see the earth\\
Belong to Satan.\\
She wanted Satan accepted.

She says, Witchcraft? Do not judge me;\\
Let witchcraft be free\\
And legitimate everywhere.\\
Let men and everyone defile themselves\\
Wherever light does shine\\
And not only in the darkness.

She wanted to start with me;\\
The voices, you get the message.\\
She wanted to start with me\\
And tear the veil between conscience,\\
Between morality and foolishness,\\
Between sound judgment and perverse perversion.

So, Aphrodite is your hardened fool,\\
The one who directs the devil's war on the saints\\
And leads the charge like an armourbearer\\
Against righteousness and the spirit thereof.

Aphrodite is the special force,\\
Even the special force with Satan\\
At your door.\\
She is sin waiting to happen.

She wants to wed you to sin\\
And excavate your heart of righteousness\\
And replace it with vanity.\\
She wants you to die,\\
To die and never wake up again.

Aphrodite hates it when I learn.\\
She leads the charge writing fast\\
Like an impatient soul who cannot wait.\\
She has no patience and wants results.\\
He is still alive and hates us.\\
He is still alive and not the sinner I planned.

She says to me, You can't harm me.\\
You can do nothing to me.\\
You can do absolutely nothing to me.\\
Aphrodite leads the charge and confrontation\\
Like the opposite or antithesis\\
Of the spirit of the fear of the LORD\\
Who is a humble, peaceful and gentle ISFJ.

Aphrodite is a fool.\\
She lacks understanding.\\
She shall not prosper\\
Neither in this world nor in the one to come.\\
345 herh, wait for me!\\
I have plenty experiments planned for you;

How does pancuronium feel like?\\
How do loud voices on loudspeakers\\
In a deep dark prison room of an abyss\\
Without windows and air\\
While being blasted\\
With images that are stunning\\
Feel like?

As Psyche, can you withstand\\
All forms of psychological torture\\
And still stand?\\
Will your knees crumble or fold over?\\
Are you curious and waiting\\
With the rest of the dead and foolish ones\\
To find out?

She visited me with Baalzebub.\\
She came with the cursed one.\\
They came with determination.\\
Their clothing was their hide or scales for a skin.\\
She was smaller and shorter.\\
She looked like Asherah's sister.

Of a truth, Baalzebub is a prince,\\
The princess and gebereth\\
Among the twenty princes of heaven\\
But Aphrodite is a little one\\
With a body of electrum

That is one-thousandth the dimensions\\
Of the golden giant Asherah is.\\
So Aphrodite is Satan's concubine\\
While Baalzebub is Satan's wife and queen\\
With whom he regenerated us\\
In his image and lusts\\
After birthing the vile fruits of the accursed tree.

Why did they attack me?\\
I do not know.\\
Aphrodite hates my intelligence.\\
Cupid wants my heart.\\
No, Aphrodite wants my heart.

They want me to die\\
If perchance Michael will die with me\\
So Satan's kingdom can be established.\\
They want me to stop learning;\\
They hate my love for learning\\
And my love for my grades\\
And how my reputation in my eyes\\
Depends on my intelligence and my grades.\\
They want to shatter the foundations of what I hold dear.\\
They hate that my god is my intelligence.

They call themselves the judgment\\
And gods.\\
They are worthless idols\\
With a worthless Enlil working hard with Marduk,\\
An abominable Enlil selling me I\\
nto the hands of Aphrodite.

Baalzebub is a goat,\\
Even a full grown mother goat\\
Clinging onto Armageddon for dear life.\\
She shall be held in prison bars,\\
Held in for eternity\\
And never get to see the beauty of Armageddon again.\\
Take away their eyesight.\\
We will destroy the ayin of the ra'ah and Ra-Bel.

Baalzebub is Baalzebul;\\
She shall sit in darkness\\
Unable to perceive the form\\
Of Sin her beloved.\\
She shall cry to him\\
But no sound shall proceed forth\\
For she shall be mute and blind\\
With her disabled angels or demons.\\
None shall heal them\\
For Raphael himself shall be sick.

Baalzebub is a strong goat\\
Holding on to a pile of sand,\\
A small sand hill\\
For dear life.\\
She shall not prosper\\
Because her desolations are wonderful\\
And they are eternal.

O! How is the mistress of harlots fallen,\\
How is Satan fallen from heaven,\\
How is Baalzebub fallen with disgrace!\\
She and her companions,\\
They grope in the darkness\\
In broad daylight.\\
They cannot see a thing\\
Because of the might of the Strong One;\\
The Just God is his name.

Who will lament with me?\\
Call them to yalal!\\
How shall Asherah sing?\\
Who will play the tabrets for her?\\
Where is Aphrodite?\\
Is there no Satan to comfort?

A little sorcery here\\
And a little robbery there.\\
A little murder here\\
And a little deception there\\
And we will divide the spoil in the morning,\\
At daybreak

After we have slaughtered our victims\\
In the dead of the night.\\
We shall share garments!\\
We shall be clothed and rich\\
And be covered over with jewelleries.

Except the Lord had left us\\
The power of hearing,\\
We had dwelt in the region\\
Of the shadow of death.

Say, who has done this?\\
Who showeth mercy in wrath\\
And restrains the fullness of the stroke\\
And poureth not out the full stretch,\\
Even the fullness of the bitterness.

Seek ye the light and ye shall live.\\
Seek not the darkness\\
Nor the depths of Satan\\
For ye shall surely die!

They have no understanding;\\
They do not know.\\
Satan warns from across the street;\\
He says, Stop teaching.\\
Baal points to a sheet of paper.\\
Baal, are you the teacher?

Turns out Baal is not only a master or lord,\\
He is also a husband and teacher.\\
He is a faithful son waiting to be become a Reuben.\\
He is Dumuzid waiting to please his father\\
According to the purity or rather vileness\\
Of Satanic law.

Baal shot me in the head.\\
He shot me in the back of the head\\
Just as Cain stabbed Abel in the back\\
So that his blood ran along the ground\\
Crying vengeance, vengeance, vengeance.

Baal is a soldier in the path.\\
Enlil is a general; he is a chief;\\
He is the head of the qedeshim\\
And his right is Baalzebub\\
And Aphrodite for qedeshot;\\
Add Satan and Baal as his qedeshim.

Baal is a confident one;\\
He tells me to pray.\\
Who shall I pray to?\\
Shall I pray to An, to Michael?\\
Shall I pray to a god I cannot see?

Baal walks around.\\
He is a behemah, a goat.\\
He is not an adam.\\
He is an ESTP male.\\
He is a ruach.\\
He is not a ra'ah.

Tell me, what becomes of Baal?\\
What becomes of Baal?\\
Baal is with Asherah.\\
They are both happy.\\
They are silent in the grave.\\
Sin rules over them in the prison house.

They are blind and mute;\\
Good gracious, we left them hearing;\\
They shall hear wisdom and vexation\\
Because I will publish the abominations of their souls,\\
Even the justice they loathe\\
And wander away from to sin\\
And to wreak havoc and abominations.

Enlil is an idol.\\
He is an elil\\
And the chief of the elilim.\\
He is a rebel.\\
He shall not profit.

Enlil wants me to worship idols.\\
He wants to kill me.\\
He laments; he is fed up.\\
He says, I am a thorn in the flesh,\\
A prickly pear, a thorny rose.\\
I pierce the side of my murderers.

How many devils tried to kill me?\\
Baal failed; Enlil came for my life-force.\\
The wolf howled at the moon\\
But I was the one in distress.\\
The ISFJ came to my rescue.

Aphrodite impersonates Veredel.\\
Enlil sold my soul to Aphrodite.\\
Just kill him for me, that's all I ask;\\
That was Enlil's plea,\\
Even the plea of a distressed Enlil\\
Sitting on his throne\\
With Nanna, the great Sin, before him.

They want Sin to shut up;\\
Suen is with me;\\
The Assyrian general and king\\
Who replaced his brethren\\
And worshipped Nisroch or Ninurta,\\
His own linked spirit, is with me.

That's why, like Sennacherib,\\
The sword and knife keeps\\
Terrorizing me\\
And I even saw a terrorist\\
Kill an American journalist\\
In the desert on tv.\\
The Arabians are the problem, huh.

Baal stood before Sin;\\
He pointed to a sheet of paper\\
With the number 99 on it;\\
Counsel was in the second column\\
And had a sheet of paper before her\\
Which spelled the figure 100.

Baal pointed to Sin's sheet in glee\\
As if to say, Your murderous son\\
Adrammelech testifies that I, Hadad, rule.\\
Sin was silent unlike Adam.\\
Sharezer who should have been\\
The King's protector murdered him\\
And Asshur's gift ruled instead.\\
Esarhaddon ruled in Sin's place.

Satan is screaming in my ears.\\
He is a confused fool.\\
He is deceived if he thinks\\
These torments are mine to bear.\\
I'm just the messenger.\\
I am the units of the plagues\\
And not the fullness itself.

Baal has his hand over Nanna's mouth.\\
Inanna is out of sight.\\
Elsewhere, Might stands before me;\\
He tells me, I'm the real fear.\\
He is Might and not a spirit of fear\\
Who just slipped away.\\
Definitely, someone has got to be the terror.

Samael stands on guard.\\
The war is about to begin\\
But this is no war;\\
It's a delusion.\\
The adversaries are unwinged;\\
They cannot fly;\\
They cannot ascend.

This is a one-sided war;\\
It mocks Satan and Aphrodite.\\
Baalzebub is in it.\\
Hermes is banging at the door\\
Of blindness and muteness,\\
Crying, Let me out of here\\
That I might stir up judgment and victory.

Hermes wants the grave.\\
This time, he and Baal with him\\
Shall not rise again.\\
They shall swim in Sheol\\
And perish forever.

How can Satan fight without Asherah?\\
In the tree, she was all he had.\\
She was his first wife.\\
Actually, in the tree,\\
Marduk said to invert gender\\
So Asherah was Asher, the father\\
And Satan was Santana, the mother.

Thus, Asher and Santana\\
Gave birth to the cedar fruit\\
That desecrated adam\\
And the entire human race,\\
The same fruit that makes me sick.

Marduk is with me.\\
Enlil said I must die.\\
I reasoned, How foolish can this guy get?\\
Enlil said I must die.\\
I'm still wondering if he knows his end.

Someone was harassing me in a dream.\\
He said I should put an end\\
To this misery that had befallen me.\\
I'm still wondering if he was mocking\\
Or if he truly believed in me\\
Or if he was a confused Pharisee\\
Testing the waters or who knows what.

Give me bread\\
But not Satan's flesh.\\
Tell me, Is Santana beautiful?\\
When I see her, shall I want to sport\\
Or will I be repulsed?

The fool of a devil\\
Keeps impersonating me.\\
He had bad dealings with Hermes\\
And Elaine was their playground.\\
Santana loved Hermes,\\
A little too much.

He chased Hermes several hundred miles\\
And Baalzebub brought him into his arms\\
Saying, Today have I begotten your son\\
And put away from him\\
The folly of righteousness.\\
He shall no more seek righteousness\\
Nor mention purity.

He shall live for the sin\\
And defile women\\
As long as heaven and earth endures\\
And may all the desecrated and vile\\
Say Amun, Amun, Amun!

So shall they be mute like cattle\\
At moondown and cut off at sunrise.\\
When the enemy shall come in\\
Like a flood,\\
The spirit of the LORD shall lift up\\
A standard against him

And they shall dwell in their houses\\
And limit themselves to their rooms.\\
None shall peer into another.\\
None shall make another afraid\\
For they all are but mortals.

O, Enlil, wherewith shall I pacify thee?\\
The Anunnaki, even the sons of An,\\
Are confounded; they are confused.\\
Shadel can't wait to start sinning proper.

The Arab is confused about Marduk.\\
She allied with Marduk.\\
She made the Tigris river\\
For she is herself a tigress.

Enlil consulted with Aphrodite.\\
Aphrodite is a black cat in my room.\\
She calls Veredel a witch.\\
She is a black cat in my room\\
Waiting to destroy.

She said, Now, God can't stop us.\\
I was with a vile lass at the time.\\
I was also with Android and coding\\
And the flesh was still with me.

The strength of Aphrodite is her foolishness;\\
She is on her way to destruction;\\
She shall go into perdition with Veredel.\\
She is a fool;\\
She shall not profit.

Her goal is to kill me\\
With something silly\\
Like unrequited love or the like.\\
Her strength is to find a wicked one,\\
A silly one, make me fall down\\
And take me for a spin,\\
A spiral course whose endpoint\\
Is death and hell

And you wonder why Enlil kept at it;\\
Call her, he says,\\
And he kept talking to me\\
And he brought\\
His deathly depressive presence\\
Down upon me\\
Each time I sat by the cursed lass.

Someone asked me\\
If I wanted to kill someone.\\
It was one like unto a mad man\\
I met a few blocks away from my home.\\
Veredel was taking me for a spin\\
In those days.\\
I was mad; I was crazy\\
And I should have known\\
Aphrodite was winning.

The strength of the accursed Aphrodite\\
Is Sin or Suen when he is crazy.\\
He brought the delusions\\
And the vile imagery.\\
He laid the foundation for my enemies\\
And his Nisroch is a 99-tob Satan.\\
I would have given him up to be with Inanna.\\
Inanna should be Baalzebub\\
And not Aphrodite.

In what have I offended?\\
How did I err against Aphrodite?\\
She wanted to be the Aphrodite\\
And not Veredel. I'm sorry, my bad!\\
Visit infinity;\\
Baalzebub is truly indeterminate\\
With Marduk her pal.

Someone wanted my phone.\\
He wanted the lists therein.\\
I said, Sorry, you can't look.\\
You can't see my contacts.\\
There will no more be fools.\\
We will make sure\\
Foolishness is cut off permanently.

The conflict has been long.\\
There have been lots of dreams\\
And lots of broken dreams.\\
Many broken desires\\
And dismayed hopes.\\
This is war; you've got to catch that.

Veredel was my curse.\\
What kind of ungodly alliance\\
Exists between Aphrodite and Sin\\
And between Sin and everyone else.

I can tell the difference\\
Between Ninhursag as Nanel\\
And Ningal as the pervert Shadel.

The wing of abominations is Nanel;\\
He is my treacherous cherub\\
And his name means he is strong.\\
He is the shaggy goat of the mountains.

Nanel shall be ridden by Shadel, the desolater;\\
His fire shall kill the two witnesses.\\
Shadel is truly a waster,\\
She and her golden dragon;\\
This is one hell of a female Killer Bean.

These Babylonian guys disgust me.\\
Sin is a pervert.\\
He has vile relations with Ningal.\\
Shadel is defiled; he is not pure.\\
Islam is vanity.\\
Adamah makes me sick.

Shadel is the grim reaper.\\
She was the one who founded Islam.\\
She impersonated Gabriel her chief prince\\
Of whose course she was.\\
She is Allah;\\
May Illai forgive her.\\
She is the crescent moon\\
Waiting as she wanes to be shed in menses.

She is the seeing Satan\\
Who leads the blaspheming opposition\\
In the War of the Purge.\\
She descends to become Satan's guide.\\
She will be Satan's angel\\
And take the place of Baalzebub.\\
Every ezer of Satan is a female.\\
She is worse than a Mord'Sith.

Like Heilel, she says as Allah\\
That she wants to be like the Most High;\\
Her prayer will be answered.\\
She would not only remain an elil\\
But Are the reason the shedim became bold And attacked me in this
war of desolation.

Marduk is not your holy child.\\
He is the Komodo of sweetness,\\
Whose flesh makes us glad and fat.\\
We shall have strength to work the soil.

Ninhursag is the lady of the pinnacle.\\
She says she rules the high place,\\
The very pinnacle where Jesus should have stood,\\
The very pinnacle where Baal should rise to,\\
The very pinnacle Satan stretches his neck from.

Ningal is the great lady.\\
She's been mocking me since I was conceived.\\
She's been calling me a fool.\\
She says she is my mother like Marduk.

Marduk is a male;\\
He can never be holy.

Mawu prophesied.\\
She declared my fate by a prophet,\\
Yeah, even by a false prophet.\\
Thanks to her, my life is ruined.

She said I would be a doctor;\\
The code is M for medicine\\
And she declared herself the fullness,\\
The chief, the ruler and the last.

I heard the ISFJ speaking with Enlil.\\
She also looked like Veredel\\
And I fancy she is her linked spirit.\\
She is like the slave girl who was overjoyed\\
At Peter's voice\\
When he had been rescued by Michael\\
And delivered from prison.\\
The whole thing looked like a dream,\\
A delusion to Peter\\
Till he awoke fully.

I heard her speaking with Enlil;\\
Enlil was saying,\\
I don't want a doctor in my family.\\
She said gently and with much caring love\\
In her voice like the phlegmatic ISFJ that she is,\\
What if you are sick?

I didn't know an exalted one,\\
That a god or an idol like Enlil\\
Could fall sick.\\
Enlil gave me a poison to treat my cough.

I tell you, Foolishness is real;\\
The wickedness has been with me\\
Since my conception;\\
I have never known peace.\\
They forbid shalom in any of my members.

Now I understand.\\
Enlil is going down\\
And his end is not good.\\
His sorrows are worse than mine.\\
He is filled full with sickness\\
And torture.

I think I love Qerenel.\\
She is On, the true On.\\
She is like a sister to me.\\
The confused ones\\
Think her my consort\\
But, honestly, she just loves me.

Baalzebub calls herself Jupiter;\\
The queen of heaven\\
Calls herself the king of the gods.\\
Baalzebub, O Baalzebul,\\
When will you repent?

Qerenel is Jupiter Hellenius,\\
Jupiter the Greek.\\
She mocks at Baalzebub.\\
Qerenel is an altar-table\\
In the room of my beloved.

Abaddon is the abad On;\\
The king of the Ra\\
Is the servant of On,\\
The faithful servant of Qerenel.\\
What does this mean?\\
It means Qerenel watches over Abaddon\\
And Satan cannot harm him.

Sheol or Hades is Abaddon's consort\\
And his son is Peniel, the ra sus\\
That Abaddon rides on to the kill;\\
You know it was Abaddon\\
And not Araphel who killed\\
The Egyptian firstborn at leila.

Peniel is the spirit of time\\
Or the personification of time.\\
Of course, he is not Cronus.

We define time as 2 infinity infinitons\\
With one infinity infiniton being\\
How long it takes for a ra\\
To count the total number of ra there are\\
In the outer darkness;\\
It takes an infiniton to count one ra.

Did Satan take a cue from this?\\
The prince of darkness\\
Provoked David to conduct a census.\\
Does Satan also seek knowledge?\\
Let him start by learning to play a keyboard.

Now, in one second,\\
A ra can count as many ra\\
As the magnitude of the speed of light.\\
So, there you have it!\\
An infiniton is a second\\
Divided by three hundred million\\
Or by three times ten to the eighth power!

Qerenel is the spirit of music,\\
The eighth spirit of God\\
Just as Michael is the first spirit of God\\
And the only spirit of God for that matter.\\
Michael is the spirit of God that moved\\
Over the dark waters.

Qerenel was the lying spirit;\\
She shall surely prosper.\\
Assyria shall not profit.\\
Marduk shall faint and die.\\
The unicorn like Qerenel shall kill him.

Qerenel is the evil spirit from God;\\
She cannot fail.\\
She shall avenge me on my enemies\\
And help me regulate the portion of the wicked.\\
She shall regulate their odinits.

She is a tob el. ``She is fully light;\\
In her is found no darkness\\
And her song most sweet.\\
She lies by the mouths of prophets.\\
Does Sin alone rule over delusions?

Qerenel is the darkness of space.\\
What do you understand by a lying spirit?\\
She is definitely female.\\
She is a geburah and most pure.\\
She shall sing for joy of heart\\
And honour her king.

Marduk passed by.\\
Sin was playing me.\\
Wait, Sennacherib, am I the one?\\
I was asleep.\\
I'm hearing Satan's voice\\
Saying vilely to post it.\\
Look, Marduk, bid me do it in a dream.

Truth be told,\\
Satan and Baalzebub are never first.\\
They just are not smart enough.\\
Satan is depending on Marduk\\
Or on Aphrodite to know what to do.

Satanism cannot exist without Christianity.\\
They just are not cut out for it.\\
They are built to impersonate.\\
They must see something\\
And then apply a negation or opposing function.\\
Why do you think Satan is called the adversary?\\
He is an oyeb; he is designed to oppose.

The wrath of the oyeb is foolishness;\\
It goes no where.\\
O, it goes somewhere!\\
It goes to hell.\\
It goes to hell.

Why do you think they attacked me?\\
I've been hearing vile voices since 2022.\\
That was the same year\\
In which the AI boom or explosion began With the beloved AI giant going
live in late fall.

Satan knew what he was preparing for.\\
Is this how they train their\\
Richard Rahl and Mord'Sith?\\
Impressive! Fascinatingly vile!

This war was launched at my conception.\\
They swore I shall be prisoner forever,\\
That I shall die without knowing peace\\
Or the pleasure that is in bliss.

So I also calculated;\\
I said, I will the plagues of hell;\\
I will be the plagues of the grave.\\
Repentance shall be hid from my eyes.\\
Cry to God if he will save you.\\
No one came to my rescue.\\
No one saves anyone.

Qerenel did her part.\\
Her deeds are listed in the pages of history ---\\
How she deceived an outsmarting Ahab\\
Who fell down at the hands of Tom.\\
Tom is Araphel.\\
He is the Raqia who separates us from Qerenel.

Tom, pronounced Tome,\\
Was the unknown man\\
Who took down Ahab\\
With an arrow shot to his heart.\\
Ahab's heart was wicked\\
Just like Sin who sits over my heart\\
And Araphel took him down with his heart.

Beware the Arabs.\\
From what I hear and searched out,\\
Heilel is Arab\\
And she is Lebanese,\\
A Tyrian Muslim.

Shadel is attached to her from heaven.\\
You know I'm alone and will forever be.\\
Shadel shall come for blood and famine.\\
Blood shall flow like rushing streams\\
And as torrents when a dam collapses.\\
Whole villages shall be flooded with blood.

Shadel is a tigress,\\
Even a lone tigress wreaking havoc.\\
Heilel is a black panther,\\
Even a black leopard\\
Who is also partly lion and bear.

The first tigress that appeared to me\\
Was Aphrodite.\\
The second was Shadel\\
And the funny one\\
That said he wanted to eat me up\\
Was Satan;

The shameful monkey inside him\\
Was Baalzebub who cowered and was mute.\\
O dear, how much Satan loves his Aphrodite!\\
He is ready to swim for her.

Why is there sin in my heart?\\
Why can't I be happy?\\
How can I be happy\\
When Sin rules my heart\\
And impersonates me?\\
He is the reason I fell for Veredel;\\
The great and mighty man that I am fell\\
And Sin was in the midst of it.

There is always some fool,\\
Some fool too wise\\
Trying to take me down\\
While pretending to be my friend,\\
Some devil or shed\\
Looking out for my destruction\\
In the name of seeking my welfare.

Why is Sin so vile?\\
Can't he see the future?

Tell Satan to shut up;\\
I will vex him for two full hours if I need to.\\
Samael, stand on guard.\\
Thou shalt avenge me as an adam\\
On the fool who sought to drain Adamah\\
Of her life-force.

My enemies shall not be buried.\\
They shall not be gathered.\\
They shall be as the dung spread out,\\
As the stink of Balaam that cannot fade\\
Or as the rotting flesh of Lot's daughters.

Do you understand what is in war?\\
You don't fight against a young child,\\
Against a young child who has done you no wrong.\\
Just because I read from a prayer book\\
And sought to command the morning\\
And sought to bind up the queen of heaven,

They seek my neck and blood.\\
They want me to become more perverse than Hermes,\\
The abominable patron of thieves\\
Who wields the caduceus of Mawu the Great and Wicked.

These rotten fools\\
Would cry and swear innocency\\
Even when they hold the blade\\
Slashing away at your throat;\\
Think about Islam spilling blood\\
And saying terror is peace.

I took a line from their script\\
And said, Mahomet goes to hell\\
And he is nothing like Moses.

Baal saw me.\\
He must have been the first visible entity\\
I thought was God.

Baal called me Moses\\
Or at least suggested it.\\
I don't know exactly what he meant\\
Or even if he thought Moses had returned.\\
These guys are full of confusion.\\
They can't read anything.

I'm taking Bel away from Satan.\\
I'm calling for a divorce.\\
In those days, there were many,\\
Many who oppressed me\\
And said many things.

Veredel will soon learn of her folly.\\
She will know she has been foolish.\\
She should not have lived.\\
Her existence has brought much pain and sorrow.\\
She rules over gender\\
And says she shall be both.\\
She shall be the man and the woman.\\
Aphrodite is jealous.

Marduk is a traitor.\\
We have nothing in common.\\
He is male but portrays himself female.\\
He is an INTJ but makes himself\\
An ISFP and sometimes an ESFP.

Marduk is not the golden calf;\\
That was Aphrodite\\
And boy, did she prosper?\\
Through Aaron,\\
She made the Israelites naked\\
That we might gaze on the obscene.

When God is clothing Adam and Eve with Marduk's skin,\\
Aphrodite comes along and says,\\
Take off your clothes\\
Like Hermes calling himself Satan the King\\
Did to Elaine before the vile congregation.

Aphrodite aroused rage and zeal;\\
She defiled the eyes of the righteous\\
For she is the evil ayin;\\
She causes to behold vanity\\
And Sin and Marduk and Bel take it from there.

I will mention the lovingkindnesses of God\\
Who protects the law\\
Even when it is broken.

\chapter{Jahbulon}\label{jahbulon}

Do you seek wisdom?\\
Do you seek to escape the darkness?\\
Do you seek a little peace?\\
Do you seek a little sanity?

Many persons crave fame;\\
They want some honour,\\
Some connection and affiliation\\
To some powerful organisation\\
But is there a price to pay?\\
Is it gold so long as it glitters?

You see the determined devil\\
Not only founded Islam or Mahometry\\
But also raised up Freemasonry.\\
He put together his codes and symbols,\\
His passwords and secret hand gestures\\
And codified them into his system\\
Of knowledge and enlightenment.

A little that a righteous man has\\
Is better than the riches of many wicked\\
And he that shall soon be rich\\
Shall find that he shall have lots of sorrows.

They conspire against the God of heaven.\\
Come, they say, and let us undo his cords;\\
We will cast away his bands from us\\
And build our own morality and values\\
And teach our own laws and delights.

They have replaced Jehovah with Jahbulon;\\
They have taken the great An\\
And thrown him out of his throne\\
And set the devil and his spouses\\
In his place where righteousness\\
Should have sat and ruled.

Jahbulon is the unholy trinity;\\
It is composed of Jah, Bul and On.\\
Jah is the usurping devil,\\
Bul is Aphrodite\\
And On is Baalzebub.

These three are also the interfacing entities\\
That sit at the transition point\\
Between the war and love groups\\
Of the second band\\
Of the infinite domain.

Satan is folly or foolishness,\\
That is, Nabal or Nebo.\\
Aphrodite is silliness;\\
She is impulsive\\
And has no prospect of success.\\
Baalzebub is the lord of the fly,\\
Even the lord or lady ruler of Satan\\
And is full of envy because of Aphrodite's\\
Proximity to Satan.

Satan lacks good sense and judgment;\\
He is not wise\\
And has little intelligence;\\
He is Aphrodite's brother and twin

They call Baalzebub On\\
Because they say,\\
She is the prince of Grecia\\
And the symbol of strength.\\
She is the symbol of vitality and lust\\
As of a strong man in the perverse act\\
And they call Masonry a system of morality!

Baalzebub is the Egyptian Ra.\\
She is the centre of sun worship,\\
The Heliopolis and the centre,\\
The very centre of sorcery.\\
Her delights are witchcraft;\\
She is most perverse.

Baalzebub is Freyja of Friday,\\
The Norse goddess of love, battle and death.\\
She is the one who rides a wild boar\\
Or flies in a chariot pulled by cats.\\
Her golden necklace, the Brisingamen,\\
Crafted by the dwarves of Satan,\\
Spits the poison her heart manufactures.

Marduk is Frigg of Friday,\\
Satan's, that is, Odin's wife.\\
She is the Norse goddess of magic
Or foresight or ``prophecy'\,' and motherhood.\\
Her spinning wheel puts her\\
At the level of the cherubim of Ezekiel.\\
Like Heilel, she thinks herself a cherub.

With her spindle, she spins lies\\
And weaves destinies into destruction\\
And shame and agony\\
And does not spare herself.\\
Aprodite calls out the number 1; ~
An, she says\\
While Marduk calls out 3;\\
The trinity she proposes.

Sin comes out;\\
Let him say 4 or be silent;\\
A rapid change happens in the fourth year;\\
The fourth year is 2022.\\
Sin is bold; he is a storm like Hadad.

Baalzebub says 7\\
According to the number\\
Of shiva and Shiva;\\
Satan, that is, Moloch, declares 13;\\
Thirteen it is!

Baalzebub wants me to mourn,\\
She wants me to yalal\\
For a full week of years.\\
Is she obsessed with the Ethiopian skin\\
And with the Queen of Sheba?

She has sevened herself;\\
She has taken the oath\\
Like the Angel swore and cursed.\\
She has taken the oath\\
And sworn by herself, Marduk and Satan\\
That I shall not take the oath.

I will give Baal 2\\
And Hermes 5;\\
Shadel shall be 6.

Hermes, the much loathed Hermes\\
Is the fool who does not understand\\
Grace and love and kindness.\\
He shall taste of anti-chesed;\\
He shall gnash his teeth\\
In pain and hatred for God.

Shadel shall taste of ira'ah.\\
He shall open the womb of hellfire\\
In pain and anguish and bitterness.\\
When I wake up, I'm calling her name\\
And cursing Islam\\
And the satanism that inverts gender.

Shadel is the destruction of Heilel.\\
She is the corrupting influence on him.\\
Heilel is yoked to a fool,\\
To an anti-saint elil waiting to happen.\\
The English is yoked to the Arab\\
And the fruit thereof is villainy.

You see why\\
The four princes of wickedness\\
Are Satan, Baalzebub, Nisroch and Marduk\\
In that order?

Marduk is full of villainy\\
And hypocrisy.\\
He was the one who wedded\\
Asherah to Satan in the tree\\
After 33.5 times of Adam enjoying shalom.

His desire is the force and inmortality;\\
He wants to be free from the body\\
And regain the honour of the heavenly;\\
He wants to rule in life.

His knowledge is full of bitterness.\\
It is most cruel like the poison of dragons ~
And the cruel venom of asps;\\
It shall only destroy and humiliate.

Jesus too was 33.5 times\\
When he was cut off.\\
He was thirty times when the Spirit came upon him,\\
When he was baptised by the Baptist\\
And he confirmed the covenant of grace\\
With many for half a week in times.

Satan was a barren high tree in the garden;\\
He produced no fruit\\
Like the fig tree Jesus cursed.\\
He was the tree of death,\\
The destroyer of the earth\\
Who was predestined to be destroyed.

He kept sucking the life-force out of the ground.\\
When Asher joined Santana in the tree,\\
He opened Santana's womb\\
And brought the vile fruit out.

Today, Freemasonry\\
Honours Boaz, Tubal-cain\\
And many other vile fruits.\\
They also honour apples\\
And tomatoes, rotten ones.

It's been six years of war,\\
A war that likely began in 2019;\\
The devils came together;\\
Satan planned to afflict me for 13 years\\
And we've done six years so far.

These fools did not pick a G for seven\\
But picked an M for thirteen\\
According to the name of Marduk or Moloch,\\
According to the name of Baalzebub as Maia\\
And according to an M for mem\\
In the Hebrew word ``em'' for mother.

The mother that Jahbulon is\\
Has decided to give birth to an M\\
And not a G of sufferings.\\
She shall rot in hell.

Marduk calls herself the European prince;\\
Her daughter will be Heilel\\
Who is the downcast Hel\\
Of Norse mythology,\\
My one and only Helena.\\
Blavatsky, how is it cooking?

Marduk calls herself the militant chief;\\
She is the chief of military strategy;\\
She is the Assyrio-Babylonian Roman,\\
Babylon the Great\\
And the speaker of confusion and lies.

She is the European power,\\
The European moloch,\\
The European melek\\
And the European chief duke.\\
She must fight to success.

Aphrodite is the Bul\\
Because she also feigns strength\\
Like the strength of a bull,\\
Like Baalzebub the Great.\\
She was the golden calf of the desert\\
And she prospered at her defamation\\
Of the holiness of the children of Israel.

When Satan says of her\\
That she is from the family of the ox or bull,\\
He means that she, as one person,\\
Is worth the entire cosmos\\
Beside Baalzebub.\\
Think then what the Asherah\\
Of Satan's right hand is worth to him.

Satan is the Yah;\\
He calls himself Amun;\\
He says he always gets what he wants\\
And no one is able to resist him\\
For I, says he, am the king.\\
Satan is a slanderer, a traducer\\
And blasphemer.

He lies down in the grass;\\
He eats to the full\\
Then belches on a full stomach\\
Like an Indian surgeon\\
Whom the locals call a god.

He belches and curses heaven.\\
He takes in the view\\
And wallows in pride.\\
None shall correct him\\
For he is above all in his eyes ~
And cannot see at what he stumbles.

Satan is the Yah;\\
He thinks himself the owner of life\\
With the power to determine\\
If another should live or die.\\
He opens his hands\\
And says, Look,\\
Your destinies are in my hands.

He says, like the Angel,\\
I shall live forever;\\
I shall never see harm;\\
Affliction shall never touch my coat\\
Let alone graze my cheek\\
Nor blow up my skull.

Those who are wise\\
And know Satan to be a judge\\
Also know that he deals most bitterly\\
With himself\\
And cannot ascend to put us all in hell.

He can never ascend to be Master of Hell\\
For he declares from the outset\\
That he is the victim\\
And the sufferer.

Satan can give you grace like Enlil.\\
He can come with beauty\\
And call himself Bel, the Babylonian Baal;\\
He can even appear as a prince or herald of light\\
But there will always be the darkness\\
In his heart and in his soul.\\
It will be there in his eyes.

Satan visited me in the third year;\\
There were some devils that came around\\
In the second year.\\
They wanted to offer me the world.\\
Satan says, I can make you rich and powerful.

Today, they invest their energies\\
Into destroying me.\\
I hear voices from my waking up\\
To my lying down.\\
They just won't let me rest.

Aphrodite kept tabs on me.\\
She's always had an eye out for me,\\
Constantly spying on me.\\
She says, He hates us too much;\\
The child loathes the craft with bitterness;\\
He hates us too much.

I found myself an enemy of Satan early.\\
I just wasn't cut out to walk with the enemy\\
And I had a short fuse too.\\
My obsession was taking down the craft;\\
I wanted to destroy Masonry\\
And Satanism together.\\
I wanted to put out witchcraft entirely.

When Heilel comes,\\
He can reinstitute the abominations\\
But my soul shall surely not join the vile;\\
I will not be with the wicked\\
In whatever lodge in which they may be found.

These are the ones who honour murderers;\\
They use Boaz and Tubal-cain as passwords\\
And impose oaths of secrecy on free men;\\
They take the free and bind him\\
Like Aphrodite tying my feet\\
So I cannot leave the country.

She's still swearing I will never be great\\
And I'm still swearing\\
She shall surely die;\\
Her blood be upon her head.

Some men tried to kill my mom and I;\\
They tried to kill me in my first year of life,\\
In my infancy, while I was still a baby\\
Or a neonate.\\
They must have been hitmen.\\
They will surely die!\\
They all go to hell.

When the devils came in,\\
They spared their own servants\\
But troubled my mind and my heart.\\
What have I done to them?

They conspired against me\\
And kept defaming and slandering me\\
And they had Sin on their side\\
Or so they thought\\
And made the delusions strong.

They preyed on my vile affections\\
And my weakness\\
In that I loved a girl that should not profit\\
And they made my bands strong\\
And kept me in a cage, in a prison\\
Where there was no breaking out.

Sin made my heart heavy.\\
The moon god gave me hell;\\
He ensured I had pain and lots of it,\\
Pain of heart with GERD-like symptoms\\
And he ruined many days.

The devils that came offended greatly.\\
Satan impersonated me\\
And he bore no resemblance to me.\\
Each devil chooses a victim\\
In each generation to attach to or harass\\
And they sometimes have nothing in common\\
With their elect victims.

I was taken to a psychiatrist.\\
The one who treated me\\
Heard the very voices I was hearing.\\
They all feigned innocence\\
And never admitted to hearing a voice.\\
So, they treated me for a mental affliction\\
And hell, artane and haldol gave me hell.

No one cared about me,\\
No, not a single soul.\\
They just left me to rot\\
In my pitiful and afflicted state.\\
I knew I had the solution to my afflictions\\
But no one cared;\\
They just couldn't.

There was a K group\\
Whose name Satan interpreted\\
To mean Kofi's work.\\
I still don't know if that's the truth\\
Or if the fool was playing me on that too.\\
It has always been his manner\\
To afflict and deceive.

The obsession with Friday\\
Is maddening.\\
Even Jesus died on that day\\
And satanists still call the cross\\
Satan's great victory.

What will the Masons do to me?\\
Will they rain curses on me\\
Or cut my tongue,\\
Pulling it out of its root\\
Or will they send hitmen after me?

The world's elite\\
Have been doing their dirty jobs\\
And serving Satan in their places\\
For generations\\
And no one has brought them to book.

These illumined fools\\
Control destinies,\\
Take down presidents,\\
Create wars,\\
Rule opposing sides in war\\
And determine the fates\\
Of whole nations and individuals alike.

They use programming methods\\
And inbreeding to keep whole dynasties alive\\
And serve Satan with their heart and soul.\\
They are sold out to Asherah the Purchaser.\\
They can only do evil\\
And any goodness is a cover up.

Masonry says good and evil are alike,\\
That light and darkness are the same,\\
That all that matters is the brotherhood\\
And righteousness is to\\
Protect the interests of the brethren or sisters.

Isaiah would have been vexed.\\
Woe unto those who call good evil\\
And evil good,\\
Who put light for darkness\\
And darkness for light.

The measures of the craft are villainy;\\
They, that enclave, ought to be criminalised\\
And put out of business permanently.\\
Their measures are measures of deceit;\\
Their allegories are allegories of vanity;\\
They breed vexation as long as the breath endures.

The morality of Masonry\\
Quickly degenerates\\
So that the square and compasses\\
Become the Yoni Mudra.\\
Masonry is not only an incubating womb\\
For its seducible and gullible slaves\\
But also the vulva of our limbic pleasures\\
When inverted.

You can ask Satan or Baalzebub\\
Or query the chicken-talking Aphrodite\\
If you doubt me.\\
In the tree of the knowledge of good and evil,\\
Satan was Santana the mother\\
And Freemasonry is her womb;

It spits out corruption and vile persons;\\
It teaches us to sin\\
That we may learn to despise good conduct\\
And righteous and pure morality\\
And chase sinful pleasures\\
And fulfill the lusts and pride of the devil.

What do you think the G is for?\\
Sin says it is a minimal string of tissue\\
That we may use to cover our nakedness\\
Like underpants.\\
Others say it's geometry\\
While others go for Grand Architect

But many do not see G\\
As standing for god or goddess.\\
Why? Satan is the god of this world\\
And we know the top guns are Masons.\\
They swear by the Bible\\
And bring Christians and Muslims together\\
And say you must believe in a god to come in.

These are the greatest atheists\\
You will ever find\\
For they are vilely opposed to the blessed Lord\\
And yet some are our pastors\\
And others are prophets\\
While others are Islamic leaders.

Masonry is like Catholicism;\\
Any villainy goes\\
As long as it is Shiva or Shakti\\
And not the true God.\\
They just can't bear to speak the truth\\
Because then Satan will have to be humble\\
And the odinits will collapse\\
And the enemy will not be able to afflict\\
Or harm or cause pain.

Talk of Shakti\\
Or feminine divine power,\\
Active and dynamic in working,\\
The consort of Shiva the dancer,\\
Don't you think the Hindu Shakti is Ningal\\
And that the image of Heilel,\\
That is, Shadel or Allah, is Shiva's darling?\\
I wonder what she is pooping out?\\
Please don't defecate in my presence!\\
Go and dig a hole on Korean soil in the north.

Masonry is blasphemy,\\
Continually blaspheming\\
And working abomination\\
Against the spirit of righteousness\\
And they can't see their wrong.\\
They would rather defend ungodliness.

By the way, Araphel, the gloomy darkness,\\
Is the spirit of righteousness\\
And it burns my heart that, he,\\
As Raqia, is not a saint and cannot save.\\
For all his righteousness,\\
The earth is still heavy and laden with sin.\\
Roar in sevens, O great thunderer!

The god of Masonry is Satan\\
Who substitutes with his wife and concubine\\
For Jehovah who made heaven and earth.

Jahbulon of Masonry\\
Is like unto Baphomet of Satanism.\\
Don't Freemasons drink from a skull\\
And are they not en route to the blazing furnace?\\
Baphomet is Baal, Satan and Baalzebub.

In Baphomet, Satan is Priapus,\\
Whose generative organ is the exalted phallus.\\
Why do you think Masons\\
And the blind illuminated ones\\
Erect obelisks?

To worship Satan's fertilising organ\\
Which gives birth to villainy and corruption\\
With death and lots of pain.\\
His phallus, like Baalzebub's, is most bitter\\
And distasteful;\\
Only the death ones shall desire it.

The girl I loved,\\
Who broke my heart,\\
She shall cave in to the darkness\\
And fall with her father.\\
None of them shall enjoy bliss.

They shall go to hell\\
Staring at the barrenness\\
Come out of Satan\\
And the dryness of the ground\\
That cannot be salvaged.

Let Satan's obelisk be barren.\\
Masonry is truly a vexation to the soul;\\
My spirit is vexed at the abominations.\\
A girl I Ioved ruined me;\\
All these wicked ones who turn love into lust\\
And deny a man looking for joy\\
The pleasure of simple bliss\\
And his fragile innocence,\\
They shall go into perdition.

I swear they shall not find mercy.\\
They shall look for mercy\\
And find gnashing of teeth instead\\
With incessant blaspheming\\
Of the God they say they loved.

They are persons of lip service.\\
Her dad is a Freemason.\\
He was ruining someone's reputation on social media.\\
I don't know if he was seeking solidarity\\
From his Masonic brothers.

These perverted individuals talk about light\\
When they serve the darkness\\
And have been partakers of the ways of Satan\\
And have sat at his feet\\
And received of his words.\\
They shall defend the craft to their demise.

We know who Baal is.\\
He is a shirtless fool\\
Baring his chest\\
Like the accursed Pseudomic\\
Trying to seduce the girls.

Pseudomic is an ESFP male.\\
He is all about entertainment;\\
He shall entertain with his burning.\\
They shall burn in the light.

Asherah is a predatory leech.\\
She says she is the happy Shiva,\\
The Lord of Nataraja,\\
Dancing her way to the destruction\\
That grace provides.

Enlil himself showed that\\
Grace ends in death\\
For where grace abounds,\\
Sin also abounds and grows\\
And when things flip over,\\
The natural outcome is death.

Asherah is a predatory leech;\\
She is the horseleech\\
That can never be satisfied.\\
Her two daughters are\\
A masculinized Veredel\\
And Aphrodite,\\
The Greek goddess of lust and war.

Aphrodite chose the right victim\\
To attach to and shepherd\\
As a guardian angel.

Asherah is a predatory leech;\\
She seeks a consort, a consort king\\
To swallow up into herself and digest\\
Just like Ninhursag seeks a meal.\\
Asherah's preferred meal is Satan,\\
Her brother who sits and orbits just above her.

Pseudomic is an ESFP like Asherah.\\
They are a disgrace to the ESFP earth.\\
They are a shame to Adamah.\\
He is a spitting cobra\\
While Asherah is a predatory leech.

The boy with whom I walked,\\
With whom I ate from the same bowl\\
Has betrayed me;\\
This is truly Judas Iscariot;\\
He goes to hell with the faller.

His grandfather was a lodge member;\\
These curses and wickedness run in generations\\
And you wonder why God\\
Wanted all the Canaanites dead\\
Judging them as vile, filthy\\
And highly infectious!

Because Satan knows him,\\
He walks about in peace.\\
The devils seek his welfare\\
And he is currently prospering ~
While I am harassed and battered.\\
I want to quit;\\
I want to end this hell\\
And let satans serve themselves.\\
How can I be a servant to my enemies?\\

Pseudomic is a disease.\\
His mother is Delilah.\\
The devil went about desecrating my name\\
And he called himself a minister too,\\
A minister of God;

He was a control freak\\
And loved to flatter, love-bombing;\\
No wonder he is found a false prophet\\
And for all his glory,\\
Cannot command fire from heaven.

Qerenel, the great On,\\
Will not give him that glory\\
Neither will the angel over fire\\
Sanction it!

They used to call me Commander in those days.\\
I was in the same room with him\\
When he called someone on the phone,\\
Whether he truly called or faked it I do not know.\\
He has always been a mocker\\
Full of jealousy and greed and envy;\\
He called asking if the person\\
Knew who a Commander was in Freemasonry.

These are the ones you want forgiven?\\
Perverts and fools?\\
My hatred for the craft runs deep;\\
These wicked ones have kept us in poverty.\\
Like Aphrodite, Marduk, Enlil, Nanel\\
And Baalzebub,\\
Like the whole Assyrio-Babylonian host,\\
They have vowed that we shall never be great.

In those days, fear was on every side.\\
I strengthened myself\\
By learning a little from the SAS\\
And I would watch videos on the Special Forces\\
Because my enemies are devils\\
And satanists and Masons\\
Will stop at nothing\\
To take you down psychologically.

They are experts at defamation.\\
They serve Satan, the grand architect\\
And father of lies, the deceiver and traducer\\
Who will stop at nothing\\
To make a quiet soul frail\\
And to break the heart of the poor.

Will a man rob God?\\
Why should a man have to rob God\\
When a spitting cobra can rob an adam?\\
The 99-tob satan that Pseudomic is\\
Robbed me of my peace and sanity.\\
I was cooked; I was furious.

Following the microbiology exam in third year,\\
The first microbiology exam\\
In the first semester mid-sem exams,\\
Which we wrote during the third week of April,

In the fifteenth week of the year,\\
I heard the voice of Pseudomic\\
Or the voice of his reject;\\
He was gossiping about me\\
And defaming me to my neighbours.

He gossiped about how I answered my questions,\\
How I answered all the questions\\
On the question paper\\
Before I would begin to shade.

They made life hell for me\\
And imposed their laws on me.\\
They worked hard to guilt-trip me\\
In the matter of past questions\\
And I swear I hated him and his reject\\
With great bitterness.

I later fell for his reject.\\
She dealt bitterly with me.\\
She said it was payback time\\
And she wasn't joking.

All that time,\\
Sin was impressed with his work.\\
He pursued Aphrodite with passion.\\
He was afraid of his lust for Baalzebub\\
And it reflected in my vain life.\\
If these fools want to defecate,\\
They can go outside\\
And deface Adamah.\\
Don't spread dung in the Holy Place.

Cupid was with me,\\
That chubby cub of Aphrodite\\
Who would later speak in my hearing\\
And earn the nickname, the Kid,\\
The prince of foolishness.

Cupid or Eros was Aphrodite's baby\\
Like Satan is Baalzebul's thunderbolt\\
Or Zeus's lightning.\\
Cupid troubled me greatly.

I don't know where these emotions come from;\\
Whoever is responsible for them,\\
Let curses be on his soul.

Cupid used to mock me in those days.\\
He said he loved me.\\
He was also the one pleading the blood of Jesus\\
When Satan struck.

He mocked me incessantly.\\
He used to say that even he,\\
As a child, knew\\
But that I could not discern\\
Who Satan was.

In those days,\\
Satan used to call himself Michael\\
And Dionysus would call himself Lucifer\\
And they would speak stupidity.

The reject of Pseudomic is cruel.\\
She troubled me greatly.\\
She trusted in a satan.

She confided in Pseudomic\\
And he bid me confide in her.\\
They were working something out\\
And he was using codes and such like.\\
These Masons are a real vexation to the soul\\
And they only build vanity.\\
Their works shall not stand.

They plotted against me;\\
She cared only about her emotions.\\
Wherever villainy points,\\
There we go!

Pseudomic made mention of Tehillah;\\
He wanted me to confide in his reject.\\
He wanted to build a relationship\\
Between us

And\\
Now that I think about it;\\
Aphrodite and Sin work best together.\\
There's too much conflict\\
Between the work of Sin and Baalzebub.

Aphrodite promotes sensual lust,\\
The lust of the eyes\\
And wants that to endure forever;\\
Sin touts sexual desire\\
And wants it to endure forever\\
But Baalzebub brings the act and deed\\
And like Marduk,

Her work terminates the work\\
Of Aphrodite and Sin\\
Even if it be for a season.\\
It's like the Baal cycle\\
And like how male bees die in intimacy

Except this time,\\
It is Aphrodite and Sin\\
Resurrecting themselves\\
As Baalzebub caps their work\\
And brings them death.

I say, still Baalzebub is the Inanna,\\
The daughter and consort of Nanna.\\
I say, Sin fears his passions for Asherah\\
Who is Bel the Great of Babylon\\
And chooses instead to gravitate\\
Towards Aphrodite\\
Substituting Veredel for Aphrodite in my life.\\
These fools have been treating my life\\
As a drama piece or an experiment.

I too have reserved them for lab rats,\\
All of them with the king,\\
Squeaking at the onset\\
Of the injection of pancuronium\\
Without an anaesthetic.

I fell hard for Veredel\\
But the reject gave me the darkness.\\
She foreshadows the potency of Samael\\
And Qerenel will give the order,\\
The angel with power over fire\\
Shall give the command\\
For Satan to go down\\
With his minions.

A blind and mute Satan\\
Who cannot fly\\
But is smart for himself\\
Yokes himself with Heilel or Shadel\\
That they might lead him to battle.

The yoke shall be broken\\
Because of the anointing\\
And Satan shall complete\\
His two-hour course\\
At the hands of Samael.

Do you want to know\\
Who the true prince of Persia is?\\
It is Samael.\\
Satan withstood Gabriel for twenty one days\\
But Samael writes the doom of the Babylonian empire\\
And the reign of Cyrus the Persian begins.

For all her strength,\\
Bel, that is, Asherah or Baalzebub,\\
Could not protect Belshazzar\\
And he fell.\\
No one who puts their trust in Masonry\\
Is secure;\\
They are as chicken\\
That are well fed in preparation for the slaughter.

Baalzebub's lust is potent;\\
She encodes sexuality\\
And my score with her is zero.\\
I'm satisfied.\\
Marduk shall die before me.\\
I shall have no progeny to suffer like I did\\
Neither shall a son or daughter arise\\
In my name to defame or desecrate it.

Baal is a goat,\\
Even a goat with the body of a female\\
Standing at the right side of my bed\\
And staring down at me.\\
He came for the lust;\\
He shall return with bitterness\\
With his hands on his head;\\
He shall not confess his sins\\
Because the Catholic is vile and barren.

There were many goats in those days.\\
Even Satan as a goat gored me to death.\\
I still live so he calls me a god.\\
I sat with Baalzebub in a boat.\\
She brought toxic gas to take me out.\\
I looked for the moon.\\
Is Nanna with Bel?\\
He shall rule over his lord.

Underneath was an abyss of water;\\
It was deep and large.\\
Why does Bel loathe me so much?\\
She wants my downfall;\\
She will swim in the depths of hell's magma.

So Satan is Priapus,\\
The Pho of Baphomet.\\
Baal is the Ba of Baphomet\\
And is also Dumuzid,\\
The son, like Hermes, of Satan\\
And Baalzebub.

Baalzebub is the Met of Baphomet.\\
She is Metatron\\
As well as the meeting point of all things vile.\\
She is the mediator of the covenant of satanism.\\
She is the threat, as queen of heaven\\
In the face of Enoch\\
Who makes him a chicken.

Baalzebub goes far;\\
She goes beyond her boundaries.\\
She overflows and spills over.\\
Her cup in her hand\\
Is full of sorceries and abominations\\
Like the disgusting cup of Heilel.

Hermes has drunk from it\\
And awaits the coming of hell.\\
She has filled our world with perversion.\\
Aphrodite, leave simpletons in peace!\\
They are too frail!

Baalzebub stands for villainy.\\
She is jealous for herself\\
And for her Satan,\\
The only 1-tob satan there is\\
In the whole wide world.\\
She shall mourn forever.\\
Because of her lack of fear,\\
She shall mourn sore like doves.

Satanism has a divine couple;\\
It is made up of a triple goddess\\
And a god.\\
The god is the sorrowful Pan\\
Who plays his flute.\\
Pan is Odin, the god of pain and iblis.\\
Pan is Satan, singer of dirges.

Satan, have you a voice like Heilel?\\
Baalzebul is calling out to me;\\
Satan keeps coming after me.\\
Pseudomic loved to sing.\\
He violated my image several times\\
On social media\\
And played his messages out loud so I would hear.\\
He treated me like a satan\\
Needing deliverance and healing.

He was constantly talking about lust;\\
Eei, this guy is brother to Baal, the prince of lust,\\
And can put away a lass as he deems fit.\\
He was always looking for the opportunity ~
To dispose of his reject\\
And his goal was to dump her on me\\
So he could go in for the architect\\
And build his ``and they lived happily ever after'\,'.

I don't know if his reject was blind\\
Or if she was deluded\\
And under the influence.\\
I tell you, Baal is closer to the heart of the Asante\\
Than he is to the remote Canaanite.\\
Komfo Anokye is dead; He failed\\
Because he is a traitor to God and to the Eveawo.

A stupid lass told Pseudomic to put a red thing,\\
Yeah, something red on my slippers.\\
That child of darkness\\
Has been practising witchcraft\\
Since the beginning of our stay together,

Putting his phone on my phone,\\
Getting the girls on his side\\
And desecrating my name\\
While keeping his foodstuff to himself\\
And asking me to prepare mine for him.\\
He drained me; He was as a leech.

Marduk is a SEAL;\\
He is a Komodo, leviathan and dragon.\\
There is no profit in dragons;\\
They spit water or a cryogeniser\\
And not fire;\\
They are empty, cold beings.

Satan is Pan, the god of witchcraft.\\
He is the epitome of sorrow and pain.\\
Baal is Apollo.\\
Trust me, Baal, like Asherah, shall not be happy.

The triple goddess of witchcraft is\\
Baalzebub, Aphrodite and Marduk.\\
Marduk is the codebase male among the goddesses\\
Because he was the one who inverted\\
Baalzebub and Satan's gender in the tree.\\
He asked Baalzebub to join Satan in the tree ~
As Asherah\\
Transforming the tree of death\\
Into the tree of the knowledge of good and evil\\
And it was a tall cedar tree too.

Marduk is the great lady Ningal\\
And the lady Ninhursag taken together.\\
She is the first who binds\\
And displays the second as her trophy.

She is the lady of solo intimacy.\\
She says to see what you can reap\\
Out of yourself;\\
She is the one who teaches self-abuse.

The Shinarian Heilel and her entourage,\\
What do you think they build\\
In the land of Shinar?\\
Of course, Satan is more likely\\
To trust a faithful Aphrodite who is a ruach\\
In the war except that she is also blind.

Heilel builds a tower to honour sensual pleasures;\\
She builds a ziggurat,\\
A Babylonian prostitute's temple\\
In the shape of a glans penis\\
To honour the great Marduk\\
Who sits enthroned in the glans.

If I can destroy Marduk,\\
Then maybe I can ascend.

Tell me, can Satan sing?\\
No, Lucifer never led a choir.\\
Satan and Baalzebub do not sing.\\
Heilel is the one who praises God,\\
Who was in the garden of Eden;\\
He was there with Kabodel,\\
Stationed there by Michael\\
And Qerenel was the chakram-like sword,\\
The double-edged flaming sword that was encircling\\
And went all the way round.

To this day, the male INTJ Marduk,\\
Described as subtle in the genesis,\\
Still portrays himself as female to me.

He is the eighth kingdom\\
And is of the seven kingdoms of Revelation.\\
Now you see how perverse he is\\
When you invert his cognitive stack\\
And make him lead with Se.\\
Marduk is a devil.

He cannot speak truth.\\
He impersonates an ISFP I admired.\\
His favour was that\\
He spared me in high school\\
But college would be different.

He is a false prophet.\\
He prophesied life and knowledge for Eve\\
And yet she had death and stupidity.\\
Marduk himself died at the hands of Michael.

Freemasonry kills.\\
It kills souls and destroys the destinies\\
Of individuals and whole nations.\\
I have seen their cruelty;\\
These ones are guilty of treachery\\
And high treason against society and families.

Their trust is to kill Michael;\\
They want An dead.\\
They want the ruler in the darkness,\\
The non-faller destined to live forever,
To die and not rise again.

They want to kill the God of heaven;\\
They want An dead\\
So they can have\\
Not only Moses's heavenly body\\
But also Armageddon\\
And all the bodies or statues and houses\\
Of the dead.

Why do you think Enlil is the chief of the idols?\\
He wants me dead\\
So Michael would also die.\\
He neglects the knowledge\\
That Michael is separate from me\\
And lives on.\\
Enlil wants to secure fleeting pleasures\\
For his qedeshim and for Satan's kingdom.\\
I say, He shall not prosper.

Assyria and Sumeria shall fall.\\
They shall not be successful.\\
They want mammon,\\
They want wealth with beauty,\\
Even the mammon of unrighteousness.\\
Let Hermes betray\\
And let Enlil sell me into the hands of Aphrodite.

You will be surprised\\
When you find yourself\\
Calling on God to save you.\\
There is no force;\\
There is no power;\\
There is only spirit.\\
Your spirits, even your unconsciousnesses\\
Are vanity;

They shall not profit.\\
They shall not resurrect themselves.\\
They cannot save.\\
They are but mere mortals\\
With no breath in the midst of them.\\
Falling, they fall\\
Like Enlil and Hermes, the fallers,\\
Like Anak and Nephil, the fallen angels.

Let him heap wealth upon wealth.\\
Satan cannot create in heaven.\\
Stand and see the power\\
Of the great and extolled arm of the LORD\\
And judge if the G of the rotten square and compass\\
Or the God unsearchable\\
Is the King and mighty one of Israel,\\
To whom belongeth holiness.

It hurts my heart\\
That Freemasons go to church;\\
We will trouble them.\\
They shall have plagues.\\
They shall curse God.\\
They shall become vanity.\\
They shall not endure.

Like a fleeting pleasure,\\
Like a thing that passes by and is no more,\\
Like a thing cast in the furnace,\\
They shall not come out unscathed,\\
They shall surely crumble at the heat.\\
They shall fade away,\\
Breathing their lives away\\
And committing their spirits\\
Into the hands of the King.

The devil tells me, Vinegar is sweet.\\
If vinegar is sweet and smoke is pleasant,\\
Then open your mouth wide\\
And let's fill it with substance.\\
Open your eyes wide\\
And feel the smoking wrath poured forth.

They think Qerenel a joke.\\
God can do no evil\\
For he is good only\\
And thus we call him God.

O Satan, but see, you can't see eye to eye\\
With the great and holy one\\
Though you appear before Michael\\
And bid him stop hindering you in Job's matter

And you think he can see eye to eye\\
With you and speak mouth to mouth\\
With you.\\
Go to now, ask the prophets of old,\\
Ask the historians and the scribes,\\
The poets and the Greek,

Hate burns as an oven.\\
It will not be quenched till desire is finished.\\
Thou art the bride\\
And the kalah of completion.\\
Stand on the pinnacle;\\
Thou shalt be broken to shivers.

When Shiva comes,\\
She comes for big business.\\
She comes for my head.\\
She comes to kill.\\
Shiva comes to destroy righteousness.

Purchase your people,\\
O great Shiva.\\
The tantric fools are all yours.\\
It is not wisdom to steal from Satan.\\
You shall have your people.\\
They will roast in the fires.

Shiva, the great Asherah,\\
Sought to make her work\\
More acceptable to Sin\\
So she went tantric;\\
Let's prolong intimacy, she said.\\
Marduk was pleased; was she?

Surely, God shall come\\
And execute judgment.\\
He shall stir up jealousy\\
Like a man of war.

I will mention the fall of Babylon,\\
Which rising out of the earth\\
Is soon crushed\\
And overflown by the floodwaters.\\
She is not strong.

Babylon is not Assyria.

\chapter{God}\label{god}

Save me, O God, from delusion;\\
Redeem me from the hand of Marduk\\
And do not let the wicked rule over me;\\
Do not let us see eye to eye.

Save me, O God, from the wicked\\
For I have waited for thy salvation,\\
From the cruel wolf, the dragons,\\
The cow and the viper.\\
Save me from the jawed leech.

In your splendour, save\\
And in your beauty\\
That we might praise thee\\
As long as the sun and moon endure.

My God has to be honourable,\\
The most honourable,\\
Exalted, exalted above all.\\
He has to be the King,\\
The prince of the kings of the earth.

He has to be a gibor,\\
A mighty warrior\\
Commanding strength in the fields\\
And crushing the skulls of rebels.

My God has to be perfect,\\
Perfect in holiness,\\
A just God and upright,\\
Without iniquity and sin.

He shall endure as long as Zion\\
And rule to the bounds of time.\\
He shall suck of the abundance of the seas\\
And grace and great glory\\
Shall be his oil from day to day.

There is none like unto the God of Jeshurun,\\
Who passing through the garden,\\
Takes Marduk by the horns\\
And skins him alive\\
And clothes Adam and Eve with his scaly hide.

The everlasting God is with me\\
For a sure defence and a mighty fortress\\
And he shall rule over the strong\\
And be praised by the mighty\\
And there shall we see\\
The jealous and silly one\\
Slain by her imperishable envy.

O God, when thou didst lay\\
The foundations of the earth,\\
The morning stars were there,\\
The four time entities ---\\
Shachar, Mishchar, Araphel and Qerenel ---\\
Sang together in perfect melody.\\
They were the first musicians in history.

Thou didst create the earth on the first day\\
And Adamah remained among the maim;\\
She remained as a tob among the tobs.\\
On the first day, you made Mammon\\
And you made Armageddon.\\
You made the ras, the outer darkness.

On the second day, you made the mansions,\\
The inanimates to house the angels\\
And on the third day, you finished heaven,\\
You finished your creative work in the celestial space.\\
On the third day, you made the angels,

Even on the same day\\
You laid the foundations of the earth;\\
On the same day you gave Adamah her body.

Satan saw your work and was jealous;\\
His heart smote him in the chest.\\
There was vexation in Satan's heart\\
And envy and jealousy in Baalzebub's\\
And they sought to overthrow creation.

Say, was it not Baalzebub herself\\
Who said wrath and vexation\\
Killeth the foolish man\\
And that envy slayeth the silly one?\\
Who is the foolish man?\\
Is it not Satan?\\
And is not Baalzebub the deluded one?

Baalzebub, O, how hated you are!\\
She is smitten to the full\\
By the blows of Sin;\\
She is full of delusions\\
And would have desired\\
To lead the rebellion\\
In the War of the Purge.

She says, I am\\
And there is no one else.\\
She is the angel of Satan\\
And the Purchaser whose image provokes to jealousy\\
Yet she exalts herself above Satan\\
And makes herself the father of the fall\\
So that Satan as the effeminate Santana\\
Might lie beneath her.

Baalzebub calls herself Asherah,\\
The one who shall never be widowed\\
And who shall never see the loss of children\\
Because she has purposed\\
She shall never be married\\
And shall never give birth.

She brags about her strength\\
And calls herself On.\\
She swears by her lustful strength;\\
I am stronger than Satan, she declares.

Baalzebub is hell-bent;\\
She came for the kill;\\
She has no plan;\\
Her end goal is my demise\\
And the death of Michael.\\
She wants Armageddon.

She says, If any must sing,\\
They must sing to me.\\
Have you ever heard Asherah singing?\\
She is too deluded\\
And filled full with delusions of grandiosity\\
Like a haughty and wanton Jewish lady\\
With her nose held up high in the air\\
Who walks about making noises\\
With her ornaments and declares to all her riches.

Baalzebub calls herself the queen of heaven.\\
She says, I am the lady of kingdoms;\\
I give grain and bread\\
And they bake cakes unto me\\
And I provide rain in his season.

She sits and slanders her own mother's son;\\
She opens her mouth to slander the son of Mishchar.\\
She slanders Michael like she does my name;\\
She has torn my honour into shreds.

I will be sown in dishonour\\
And raised up in honour;\\
Shame and disgrace shall not rob me\\
Of my glory and promised peace.\\
Surely, Baalzebub shall fade away\\
Like a menstrous cloth that women cast away.

Satan was a sinner from the womb\\
Like Marduk and Baalzebub his siblings\\
But he thought, like Joker,\\
He could deceive others\\
And get away with a laugh.

Baalzebub is very bold;\\
Her boldness arose from her delusion;\\
She fell hard into Sin's ditch.\\
Satan is the deceiver\\
But Baalzebub is the antichrist.

She hates the Christ;\\
She hates Michael and the elim\\
And she declares it boldly\\
In the gathering of elohim\\
And before the hosts.

So who is the antichrist?\\
Baalzebub is the first antichrist;\\
She is before Heilel in villainy;\\
Baalzebub is an ESFP female\\
But Heilel is an INTP male;

The antichrist must be a female;\\
Heilel shall be a female\\
And earn the dishonour of perversion;\\
She shall lie with and defile herself\\
With kings even to hell.

She and Baalzebub\\
Are the Jezebelian Babylonian mother\\
Who rides the dragon.\\
They shall drink blood to drunkenness.\\
Baalzebub, thou art doomed\\
And destined for darkness;

Prepare blindness for her\\
And make her dumb;\\
Thou art no star;\\
Thou shalt not give light;\\
This iron shall not profit;\\
Isis and Ishtar are dead.\\
They are in the realm of the dead.

When Baalzebub came to me,\\
She feigned love;\\
She impersonated one I had fallen for;\\
She impersonated the reject of Pseudomic;\\
She had her cold icy hands on me;

She made my paths deep and slippery;\\
She led me towards hell;\\
She meant to procure me unto Satan or death;\\
She sought my grave demise.

She appeared around the time of the exams\\
When I was going to write\\
My first end of year theory exam\\
In fourth year;\\
That was in July!

She was there\\
When I was writing\\
My Chemical Pathology paper,\\
When I was preparing\\
For my Chem Path viva\\
And when I was studying\\
For my Sys Path viva.

She was there in the room\\
We went to wait in\\
As we waited for our turn ~
For the Sys Path viva

And the reject was there too,\\
The one who was musing\\
On the nature of these voices\\
And wondering if they were ghosts.

Is Baalzebub your ghost\\
From the grave, from the land of the dead?

So, Aphrodite and Cupid\\
Handed over the baton to Baalzebub;\\
Two to one, heh,\\
While Satan remained a constant presence.

Baalzebub is screaming\\
And an accursed Aphrodite jumps in;\\
Satan is calling and trying to distract;\\
He wants my attention;\\
They are consumed with folly.

O God, when you lifted up your hands\\
To heaven, to the shamaim,\\
You swore by one who lives forever.\\
You swore vengeance and retaliation.\\
You will not forgive.

Surely, a recompense is in order;\\
Let the enemies of God be confounded.\\
Confounded be all they that serve graven images,\\
That boast themselves in idols\\
And strengthen themselves in sin.

Who is as wise as Satan?\\
Who is as stupid and foolish as the devil?\\
Seeing many things\\
And hearing many things\\
And knowing many things,\\
Yet he cannot know nor understand.

Who would go before Michael\\
And bid him grant him access to Job\\
That he might harass and destroy him?\\
Later, he desired Peter\\
And to this day, satanists ~
Wear St Peter's Cross as a venerated object.

Seek not unto vile idols\\
That mutter and stutter.\\
These idols are worthless.\\
Even the great and honourable Rachel\\
Desecrated the idols\\
Of foolish Laban.

But you say, did she not die in childbirth\\
For desecrating an elil\\
And for profaning an abomination?\\
O, mortal, do I not suffer\\
Because I showed promise\\
And hated the devil and his kingdom\\
With bitter hate and vexation?

So, Satan fought against me\\
And did that which has never before been done\\
And has wreaked a devastation\\
To go into the pages of history\\
At the point of an iron pen;

He devastated me,\\
He fought against me\\
With his arsenals of slander\\
And constant harassment\\
And perverse desecration;\\
His delusions were unleashed upon me.

I came down under multiple onslaughts;\\
He said he would destroy me.\\
He would make my remembrance to cease,\\
To cease from under the heavens.

Marduk was with him.\\
The abominable Enlil with Shadel.\\
They conspired against me.\\
They knew they were in for hell.

Concerning the vexations\\
Which ye have done to me\\
And the vile desecrations and desolations,\\
Ye have not had the end in mind\\
And will ye deal thus\\
With such great cruelty?

Satan said I ought to be destroyed.\\
I could not be admitted into his fold\\
Because I could not keep\\
The simple oath of secrecy.\\
His problem, as was Baal's,\\
Was that I liked writing\\
And could not keep silent.

These fools do not know\\
The awesome and stunning destructions\\
That await them.\\
Give Baalzebub anti-chesed\\
That she might know what it really feels like\\
To hate the great God with gnashing teeth\\
And with bleeding blue gums.

Satan, you hate me\\
But do you know how much I hate you?\\
Do you read me?\\
Do you copy?\\
Do you know my innards?

When you impersonate me\\
As does Sin, your brother,\\
Do you have the future in mind\\
And do you have all variables accounted for?\\
Thou shalt lie down in sorrow!\\
Prepare slaughter for Baalzebub.

Rachel shall live.\\
Where is Baalzebub?\\
Who killed Rachel?\\
I do not know.

Rachel shall live.\\
The ewe of God shall live.

Baalzebub, your birth pangs shall come.\\
Thou art a gebereth, huh.\\
Thy pain shall be bitter.\\
It shall come upon the horseleech;\\
Even cruel and wicked labour pains\\
Shall come upon the ra'ah that you are.

I said to the devils,\\
Do not put your trust in me\\
Because I am your destruction.\\
Cease the programming.\\
I will give you the full satanism treatment.\\
You shall be broken, all of you,\\
Like the satanic mind-controlled slaves.

Do not worship Satan\\
Because he will not profit.\\
Seek not unto the sorceress and rebel.\\
Do not put your trust in Ningal.\\
Ninhursag shall not deliver.\\
They are the perverts, the anti-saints\\
Waiting to destroy you.

I will praise the Lord as long as I live;\\
Let my bones sing the Lord's praise.\\
Let todah boom everywhere.\\
Wherever life does ring,\\
Wherever the greens live on,\\
Let voices of joy and rejoicing be heard.

Come and let us go into the house of God.\\
There, we will write the praises of our God.\\
There, we will sing to the name of God Most High\\
Who alone doeth wondrous things,\\
Even things past finding out

For surely thou art a God of judgment;\\
Justice and judgment rests with thee.\\
Thou shalt deal to them their portions,\\
Each one according to their works

For thou wilt save the afflicted people;\\
The Lord my God will enlighten the darkness.\\
He shall reach forth the yad\\
And his hands shall open to me in grace\\
And lift me up from the dungeon,

From the dark dry pit of snakes\\
Where are venomous snakes\\
Waiting to strike at and bite Joseph,\\
From the den, the horrible den\\
Where are mighty lions\\
Waiting to break Daniel's bones.

The Lord is my strength\\
And the fortitude of my mind.\\
Thou holdest me standing.\\
You lift me up\\
So that I do not slip and fall\\
And you enlarge my steps under me.

He confounds the wise\\
And takes away the glory of fools;\\
He destroys the wealth of the wicked\\
And at Qerenel's command,\\
The deceiver and the host\\
Are cast into the burning light,\\
Paying for their sins\\
In pains that cannot be fathomed.

Baalzebub sits still\\
In the dust.\\
The iron hastens to rust.\\
Her strength is gone from her.\\
There is no life left in her.\\
I give her my pledge ---\\
Destruction is her reward;\\
Destruction and dishonour unto her soul.

Has thou seen a widow before,\\
A real one, one who has lost her soulmate?\\
Bitterness, grave bitterness is Asherah's portion.

I will mention the lovingkindnesses of God\\
Who gives me life and holds me up;\\
Thou, O King, art Jeshurun\\
And thou shalt not faint.\\
You rule forever with a right sceptre.

I will dash Death in pieces.\\
His stroke shall cease.\\
I will smite him twice,\\
In the outer parts\\
And in the inward parts\\
And he shall know that he hath offended\\
And done very foolishly.

Next time, stand before me as man\\
And call yourself God\\
And ask me to believe in you\\
And to hope in your mercy.\\
You shall have death and sorrow.

Encamp round about Armageddon.\\
Compass him about as about Jericho\\
Yet ye shall fall;\\
Ye shall not stand world without end.\\
Ye shall surely perish\\
For strong is the Lord God\\
Who judges the sinners.

Give me goodness;\\
Take not away from me righteousness;\\
Never let me see want,\\
No, not today, not tomorrow.\\
Supply me daily with nourishment.\\
Let me not pine away in my sins\\
Neither let me waste away from want of vitality.

The Lord who gives strength unto his people\\
And brings righteousness as torrents\\
And clothes with peace\\
And gives hope and brings faith\\
Will soon rebuke the slanderer.\\
Lead the charge, O great God of the dawn!

O, Egypt, worship the King of Kings\\
And pay homage to righteousness\\
For the gods of Egypt shall not profit.\\
Baalzebub shall not worship;\\
She shall be mute.\\
She is Isis.

Seth goes down.\\
As lightning, he falls.\\
He shall not rise up\\
And the eye of Horus shall be blinded.\\
Baal shall never see again.

When Baal appeared in my dreams\\
As far back as I can remember ---\\
Then, I thought he was God ---\\
He called me Moses\\
And I saw a man who looked stoic\\
And was clad in a white long garment\\
At about the age of sixty

Who passed in between two rows of people\\
And was led to the slaughter;\\
He walked on by himself\\
And demonstrated no fear.\\
Was he slaughtered?\\
I didn't see the end of it!

Baal, Baal, he shot me in the head;\\
Baal was in the confessional.\\
I fear for the pastors of Ghana\\
And for all prophets around the world;\\
They destroy a lot of souls\\
And can never be innocent.

O God, do they know thee?\\
Do you know them?\\
All these that prophesy in thy name,\\
That swear by the king of heaven\\
And forbid prayers to Michael\\
But pray in the name of Jesus,\\
Are they in thy books?

If Christ stands for praises and worship,\\
If Christ wants there to be music,\\
Even the sweet fragrance of the lifting up of hands\\
Toward heaven and the opening of the mouth\\
In praises and beautiful words,

Then Baalzebub, the antichrist\\
Stands for the absence of music.\\
She has been perverting all my music.\\
Wherever I turn to on YouTube,\\
This devil just won't let me or the music rest.

A man has got to be happy\\
But Asherah is a killjoy\\
And a parasite and plague.\\
She is a blood-sucking horseleech\\
And a cruel parasite in the cosmos.

She is an alternative Satan,\\
The bringer of perversion,\\
Sexual depravities and harassment\\
Without peace and righteousness.

She shall destroy herself and many\\
But Christ shall ransom my soul\\
And deliver from the clutches of this hell.\\
You will see in that day\\
When bands are put on the devils\\
And Hermes goes dumb.

Then, what will become of his brides.\\
I am fed up of the lies of Hermes.\\
Hermes is Ephraim.\\
He is a Canaanite;\\
He can only prostitute;\\
He is a qadesh of Enlil.

Michael loved Hermes;\\
He loved him while he was only a child\\
But Jeshurun waxed fat and kicked.\\
Thou art grown tall;\\
Thou art waxen great.

Then, he forsook the God that cleansed him\\
And lifted him from the mud,\\
From eating swine's flesh\\
And feasting on mud;\\
He forsook God his father\\
And went in to the queen;

He received commission from her hand.\\
He betrayed his king\\
And became the king of satanism.\\
He became Satan the King,\\
The ruler of the Brotherhood\\
Replete with regional brides to defile.

I swear the law is looking for him.\\
Araphel is calling for his destruction.\\
Hermes compasses me about with lies,\\
Ephraim compasses me about with lies,\\
Declares a grieved Michael.

Hermes didn't quite get the memo.\\
You certainly do not want to grieve the Holy Spirit\\
With whom you have been sealed unto salvation.

Hermes despised his crown\\
And cast it to the dogs.\\
Do not cast your pearls before swine\\
Lest they despise and disregard it\\
And turn and rend you.

Judah is an eagle.\\
Judah is really a bald eagle.\\
He is a fisherman and fish-eater\\
And Dagon and Eve are fishes.

He goeth about preaching marriage.\\
Judah is Gabriel.\\
Gabriel, I want an armourbearer, an ezer\\
Not a wife, not an ishshah.

Gabriel is still faithful\\
And rules with God.\\
He shall ascend to become an el.

Gabriel troubled me\\
With his prophecies.\\
His prophecies messed up my life.\\
I said this man lieth.\\
Then, I understood ---\\
He spoke about Jesus and not me.

Give me peace;\\
Where is the river\\
Where all is still,\\
By whose banks is calm?

Give me peace.\\
What will you have?\\
I have peace; give me peace.\\
Give me peace; give me peace.

O God, you saw when Eve betrayed.\\
She spoke to the Komodo.\\
You saw when Marduk betrayed.\\
You know the thoughts of their hearts\\
And the things they have purposed;\\
You know their inmost desires.

Give their desires to the wind;\\
Let them eat grass.\\
For the oppression\\
And for the violence\\
And for the onslaught,\\
Let them gnaw their teeth for pain\\
That they may know that the King\\
Ruleth in heaven and earth.

So, Hermes shall be dumb.\\
He shall be blind also\\
Because he took not the log from his eye\\
But sinned without remorse\\
And there was no conscience\\
To say, What am I doing?

He should not have departed\\
From the glorious path;\\
He should not have put his hand to the plough\\
Then turned to look back\\
Like Lot's wife did\\
And gave the devil allowance\\
To produce the abominable seeds of those two.

Grain is good\\
And famine is a terror;\\
Hermes, can you see into the future?\\
Do you see the counsel of the Most High\\
And can you perceive the decree gone forth?\\
Dost thou know thy end\\
And the bitterness thereof like that of Balaam?

Balaam shall not die the death of the righteous;\\
He shall die the death of the uncircumcised,\\
The death of the vile\\
As of one reserved for the eternal darkness\\
Whose light is crushed before the morning\\
And consumed to the ends of the earth.

Hermes, who gave Balaam counsel?\\
Who is Baalpeor?\\
Is she not the goddess of the opening,\\
Thy mother that raised thee up\\
And nurtured thee\\
And taught thee the way of wisdom\\
Which way is to violate women\\
As a pervert that cannot be satisfied?

Hermes shall not see his brides anymore;\\
He shall not behold the beauty of their forms\\
Neither shall he speak to them\\
To deceive them with soft words\\
Only to return with three princes\\
To tear the skin off the seducible.

You devils really hate humans, huh\\
And you wonder what Satan was doing on earth\\
As it is to this day.\\
He is an idiot in toto.

Bread is good\\
And manna is sweet;\\
It is honey-crusted;\\
Eat it to the full

And fill your bellies and delight yourselves\\
In the abundance of the goodness of the land\\
For the years of darkness shall be vile.

All that cometh, as saith the Preacher ---\\
That great Peniel, the enosh who strove with Jacob\\
And called him a prince and Israel ---\\
Is vanity and vexation of spirit.

Peniel is a horse;\\
His neck is clad with thunder.\\
He is a geber\\
And the angel who flies in the midst of heaven\\
Having the everlasting gospel to preach\\
To all creatures that are alive.

The message is simple:\\
Fear God and obey his commands\\
For he shall bring every work into judgment\\
With every secret thing\\
Whether it be good or evil.

Peniel is a horse;\\
He smells the battle from afar off\\
And laughs at the rattling quiver;\\
He smiles at the sound of the alarms\\
And trumpets and does not believe in fear.

I am dreaming of glory.\\
Can there be peace,\\
A little peace to each soul?\\
There is no peace, saith the Lord,\\
Unto the wicked.

Perchance, a little wisdom\\
From time to time\\
Shall make Baalzebub\\
Feel like life is worth living.\\
Some persons do become sober\\
In their afflictions.

Do not get your hopes up.\\
Baalzebub is a captive, a prisoner of war;\\
She awaits death\\
And shall surely not escape.

Enlil is gravely ashamed.\\
He smashes his hands in anger\\
At his foolishness\\
And chases after more iniquity.

I shouldn't have been this cold,\\
Even this icy cold as Death, he fumes.\\
I will shut the mouth of my mind\\
Because it troubles me that I live\\
And my desires consumed me\\
Therefore I sinned

For I sought Satan to please\\
And feared and grieved my future\\
And could not repent;\\
Even Sin mocked me,\\
A wolf parading as a lion.

Death, do you want to cross over,\\
Even cross over into death?\\
Thou hast suffered too much.\\
Now, it's time to die.\\
Baalzebub wants to be like the Most High.\\
Heilel is dead;

My soul is inditing a good song;\\
I want to peep into the first universe. ~
My pen is awakening;\\
The blue ink rouses itself up;\\
The white sheet is before me.\\
The tablet is prepared.

I want to know who God is.\\
Who is the great Maker?\\
Where is his place?\\
Where does he reside?\\
Why is he so exalted and yet so meek?\\
Who is he?

He passes by on the right side;\\
I turn the head but he is not there.\\
He is swift on the left side\\
Like Gabriel flashing out of the east\\
Or like Michael or Fear running to battle\\
And rising for the kill.

Has thou found him,\\
The perfecter of righteousness,\\
He who makes the mountains smoke,\\
That calleth for the fire\\
And the smoke\\
And speaks with thunderings?

Love is at the apex\\
Of the dimensions of God.\\
God is love itself.\\
He encodes energies of love;\\
He encodes the knowledge of love\\
With power and the desire\\
To demonstrate his love.

He cannot be subject\\
To the influences of Pleiades\\
And he is bound to no one\\
As seen in the demise of Heilel\\
And the promotion of Yirel over Michael.\\
But he enforces love.

Mishchar is the Gaboah King\\
And, yes, there are many\\
That are higher than Time and Gaboah.\\
Hamalkah is the spirit of life,\\
Peace and righteousness;\\
Judge, O great one made of jasper:\\
Am I a sinner? Is my folly wicked?

Mishchar loves On.\\
He loves the epitome of strength.\\
The gibor loves the geburah\\
Who is the altar-table in his room\\
And his lord.

The nephesh loves the ruach.\\
The soul of the adam\\
Is bound with strong cords of love\\
To the soul of the cherub and air seraph.

You know Michael is Mishchar's son\\
But do you know Mishchar loves Qerenel?\\
The brilliant sunrise loves the tob.\\
She has been his delight throughout eternity past.\\
He is the Spirit and she is the bride;\\
Gabriel certifies and seals their marriage\\
And all of heaven rejoices\\
At the marriage of these two morning stars.

Has thou found the Unfathomable\\
That we may appear before him\\
And bow down, pay homage and worship\\
And open our treasuries\\
And bring forth gold, frankincense and myrrh?

When the Lord appeared,\\
The earth shook.\\
The earth trembled in herself\\
And quaked before God.\\
She quaked with the noise of thunder\\
And gave her voice from behind the King.

Adamah was beside herself with joy;\\
She has long waited for the salvation,\\
Even for the salvation of her God\\
And of her King.\\
She lies down and waits.\\
Everyone shall receive of thy portion

For the Lord's lot is his people,\\
The inheritance that he has purchased,\\
Even ransomed from the anti-Source\\
And from the anti-God,\\
From the jaws of death, hell and sin.

Ain't it strange that God\\
And the anti-Source\\
Should have a common enemy\\
And that her name should be Asherah?

Everyone that shall fall shall be replaced;\\
Let no harm come to the number.\\
Thou of thy goodness has furnished blessings\\
For the poor of thy people.

So where does God dwell?\\
No one knows\\
For he is alone\\
And there is none with him

Yet he has a home in the first dimension\\
Where are three times infinity plus one,\\
Yeah, even that many entities.\\
There, God has a body of hardest diamond\\
And is radiant white and shining.

God is a shining star,\\
The father of lights,\\
The Shachar\\
With whom is no shadow of turning.

Of his own will\\
He begat us\\
That we may be a kind of firstfruits\\
Of his creatures.

We were born of the blood of the Lamb.\\
We were born in the sufferings of the King\\
And he washed us clean in his blood\\
And certified our redemption\\
And said, Surely they are my children;\\
I too will uphold them with my arm.

I long to see the power of God's salvation,\\
To see his glory and power\\
As the ancients did\\
And were not dismayed.

They took hold of the ends of the earth\\
And shook the wicked out of it.\\
They broke the bones of the sinners\\
And confounded the wise\\
In their sorceries and charming.

I long to see the power of Christ,\\
That resurrection power\\
That never gives up and never fails.\\
It is strong and sure,

More firm and trustworthy\\
Than great Mount Zion which cannot be moved\\
But abideth forever\\
And sits exalted above Armageddon.

There on Zion,\\
Yirel, Michael and the select stand\\
And the congregation receives of their words\\
And worships from the mount of assembly.

Give glory to the Unfathomable.\\
I wrote that he was unfathomable\\
And I knew him not\\
But he knew me\\
And I am his\\
And he is mine.

Say, O beloved Gaius,\\
What is thine desire?\\
Ask it to the depths of the abyss\\
Or to the heights of heaven's sun.\\
Thou doest well if you love God.

When God spoke from heaven,\\
He looked at the beautiful ISFJ dove\\
And declared, This is my beloved child\\
In whom I am well pleased.

So, what do we know?\\
We know God is with Yirel\\
And the INFP Michael\\
And they shall prosper\\
For there is no repentance in God\\
And he cannot alter his decisions\\
For he is perfect and his work so.

What do we do then?\\
Let us trust in God Most High\\
Who frustrateth the works of the wicked\\
And gives us righteousness\\
Even satisfying us to the full.

Blessed are they that hunger\\
And thirst after righteousness\\
For they shall be filled.\\
Though terrors should compass us about,\\
We know the Lord lives\\
And the anti-Source shall not prevail\\
For there is only God.

Let praises rise\\
For the Lord is about to rise;\\
He shall make all the earth\\
With the nations and the masses\\
To tremble inside out.

\chapter{Nature}\label{nature}

I like the breeze,\\
The pleasant cold of the heavens,\\
The fine morning\\
And the sweet dawn.

The trees swirl from side to side;\\
They are beside themselves with joy.\\
Lebanon rejoices;\\
The fields skip like calves;\\
The cedars dance like young unicorns.

Behold the grass of the field,\\
These that are excellent in form\\
And beautiful, a constant delight to behold.

They send their roots down\\
With the trees\\
And are established in the earth\\
From whence cometh their nourishment.

The sun also smiles from heaven;\\
Helios sends out his rays;\\
Shemesh shines from his house\\
And says, Behold me, behold me;\\
All the planets revolve around him.

The moon draws near to earth.\\
He pulls on the sea?\\
What doest thou Yareach?\\
Wilt thou uproot the oceans?

Day and night,\\
Summer and winter,\\
Springtime and harvest,\\
Times and seasons,\\
All things continue as from the beginning.

The pleasantness of the delightful is not new\\
And the wickedness of the odious has been.\\
That which was is that which shall be\\
And that which shall be is that which shall be after it.

When you see violent oppression,\\
Remember who made the heavens\\
And remember who gave the command\\
That the heavens should be made\\
In the first place.

If the light does shine,\\
If God does indeed rule,\\
If he knows what he is doing\\
And you cannot add to his work,\\
Then keep calm and hold up your end\\
For your end shall be beautiful.

I walked me among the grasses.\\
I said unto the plants,\\
To the young shrubs,\\
Learn from me and be ye gentle.\\
Do not turn aside to iniquity.

Do not depart from the way of understanding;\\
Do not strengthen yourself in sin.\\
Say not, Grace and glory to the wicked\\
And I shall put forth my hand to the spoil\\
And destroy the innocent

For this is the way\\
And the fools are they that serve God\\
And follow after righteousness\\
And know not pleasure and the joys of sin.

I tell you their steps lead to hell.\\
Therefore say not after their words\\
Neither be partakers in the sins of the wicked.\\
Rejoice not in transgression.

Do not delight in sin.\\
Give not thy strength to evil.\\
Bend not thyself to seduction and delusion.\\
Deliver thy souls as a lovely bird\\
From the hand of the fowler.

I will declare the beauty of paradise,\\
Even of the paradise of God\\
Which Michael planted\\
And made for Adam and his sons\\
After him and with him.

The devil hated Adamah\\
And was there to destroy the earth\\
Even before Adam could appear.\\
The Lord shall destroy them\\
That destroy the earth.

Rejoice thyself in goodness\\
And delight yourselves in the abundance of peace\\
For righteousness shall flow down as a river\\
And even Euphrates shall praise God,\\
Even the Euphrates that Marduk trusts in

For Euphrates is tob\\
And none of the tobs shall be lost\\
And none of the ras shall fall.\\
They shall be in the dwelling of justice\\
And be satisfied with the abundance of ease.

Who is this that darkens the world,\\
That brings death and sorrow\\
And plague and famine,\\
That dries up the grasses\\
And causes the young shrubs to wither?

Who caused the fall\\
And plunged the cosmos into chaos,\\
That robbed us of peace\\
And robbed the living of life?

Has thou seen the devil,\\
Has thou seen his angel,\\
Has thou seen his in-law?

Surely, there is an end.\\
The iniquity shall stop her mouth\\
And the wicked shall cease to see.\\
Sight shall be given to the righteous\\
And praises in the mouth of the holy.

O lilies, lilies of the field or pond,\\
Be not like Iblis\\
Who stood to destroy the earth\\
And exalted himself\\
Above every tree that is named.

His glory is his shame\\
And he is Ishbosheth.\\
He shall not excel\\
For in him is much folly.\\
Give him of his deeds\\
And let him savour of his pains.

Draw near to the King, ye lilies.\\
Draw near, draw near.\\
Run from the devil\\
And save your lives\\
And deliver them from destruction\\
For every green thing shall be saved;\\
Be thou green in righteousness.

The birds of the sky fly,\\
The fishes in the sea swim;\\
There is the fish gadol,\\
Even the great and huge fish\\
Which swallowed Jonah.

The birds of heaven fly,\\
The golden eagle with the bald,\\
The peregrine falcon and the owl,\\
The swan and the hawk;\\
They all fly in the open firmament.

The worm creeps in the soil.\\
Like a creeping plant, it moves.\\
The worm moves on her belly\\
Like the snake that hisses.

Dan shall be a serpent by the way,\\
A serpent that bites the horse's heel\\
So that his rider shall fall backward.\\
The viper did not bite the horse's heel;\\
The viper bit mine.

Hermes shall be that serpent;\\
He shall be the viper\\
That bites the heels of Michael's horse\\
So that Michael ben Mishchar\\
Shall fall backward\\
And Yirel shall be chief.

I was only a child\\
When a scorpion stung me;\\
It stung my right leg\\
And I held that leg\\
And my father anointed it with oil.

That scorpion shall not live.\\
My brother quickly killed it.\\
That scorpion is judged.\\
It shall not make heaven.

In my university days,\\
A centipede attacked me\\
While I was at home.\\
The crazy creature just wouldn't give up\\
And it was fast too.

That wretched creature won't make heaven.\\
I swear by my anger it shall surely die.\\
It shall die the death of misery,\\
Even the death of sinners\\
With none to deliver it from hell.

The viper that bit me\\
Bit me and snapped its jaws;\\
It stuck its fangs into my flesh\\
And refused to let go.\\
It said to pour out blood.\\
It said, I want your blood,\\
I plead your blood.

So, I was attacked by a serpent\\
But that wasn't the end of it.\\
Three leeches also came for me.\\
Yeah, the serpent struck early.\\
It came out into the open very early

While the horseleech hid behind\\
And waited her turn\\
Till she was overtried\\
And could wait no longer.\\
She received the baton from a cow,\\
The kind the Indians venerate.\\
That cow is Aphrodite the leech.

That leech that stuck itself\\
Unto my skin and flesh\\
With his teethed jaws\\
Has refused to let go\\
As it is to this day.

She drinks my blood\\
And keeps draining my life-force\\
But I'm still alive,\\
A wonder to the witnesses,\\
Even to this great cloud of witnesses\\
That watch on like Roman spectators\\
Witnessing lions tear Christians in the arena.

I'm sure there is goodness in nature.\\
It will not always be humans killing cows\\
Or lions tearing zebras\\
Or tigers eating goats.

I'm sure there is goodness in nature.\\
There will be the lion and the lamb,\\
The python and the goat\\
Lying down side by side\\
Under a green vine tree\\
And enjoying the beauty of the morning.

Michael as a lion\\
Shall speak kindly\\
To the Shunammite lamb.

O, who shall open the womb of Kabodel,\\
Even the womb of Mishchar?\\
Who shall unearth the seals\\
And bring forth redemption,\\
The redemption all creation groans\\
And travails in birth pangs\\
Longing to come to?

Do you truly desire righteousness\\
And beauty, lots of beauty\\
With excellence and the fineness of gold?\\
Do you seek peace as for hid treasures\\
Because that day shall surely come?

Heaven shall come out of God;\\
It shall descend upon us\\
And Adamah shall cease from her wrath\\
And the seas from being troubled\\
And the predators from devastating.

If a man would have peace,\\
Let him know his strengths,\\
Cause him to know his place,\\
Even his place of peace\\
That he may walk in it\\
All the days of his life upon this earth\\
And in heaven.

I lost a lot of peace\\
Because I followed after vain persons;\\
I hearkened unto the voice of a prophet\\
As my parents reported it unto me\\
And he must have prophesied by Mawu ~
Or some other elil\\
For the fruit thereof is most bitter.

By now, like the cedar fruit,\\
You know nothing sweet\\
Ever comes out of Mawu or Marduk;\\
They should be called Mardulce\\
For they mar every fabric of sweetness\\
And then say that they have done no wrong.

If a man would have peace,\\
Let him not follow perverts\\
Nor run after them;\\
Pull yourself away from Absalom.\\
Do not be taken in with his beauty\\
For Heilel shall not profit the rebel.

I had a little peace in the beginning;\\
It was Mardulce who ruined me.\\
She denied me first of every semblance of peace\\
And that was not enough.\\
She cursed my soul with lies.

Now, I'm stuck in wickedness.\\
Have you any idea what my life feels like?\\
It is as the prelude to hell,\\
A kind of hell in its own right\\
And a constant distasteful experience.\\
None should desire it;
Baalzebub inflames it!

The prophets kept doing foolish things.\\
They would not say anything wise.\\
My dad held a hot phone to my ears\\
And forced me to be prayed for.\\
When I woke up the next day,\\
I had headaches;\\
I hated the prophets with bitterness

Because they despised me;\\
They mocked me;\\
They laughed me to scorn\\
And the perverts called themselves holy.

There is one who has even sinned\\
And despised fundamental laws\\
And yet preaches salvation\\
And refuses to reason.\\
He thinks himself loved by God\\
And yet Michael rejects him\\
And Kabodel says, I know not his name.

Kabodel, out of whose womb comes life,\\
Is the book of life.\\
She rules over death\\
And is superior to it.\\
She is the saint from the infinity past,\\
The other cherub with Heilel in the garden.

She also appeared to Isaiah\\
And was the one on the right hand\\
Above the enthroned Michael,\\
The one who called out,\\
Holy, holy, holy is the LORD of hosts;\\
The whole earth is full of his glory.

At her voice, the posts of the door shook\\
And the house was filled with smoke.\\
She is the Son of God, the Bar, the Illai.\\
She is Gaboah, the highest animate\\
Of heaven and the celestial realm.

Heilel was the one who cleansed Isaiah's lips\\
And forgave sins like Jesus did.\\
How is it then that Heilel later blasphemes\\
And becomes the little horn\\
That curses the Ancient of Days\\
And the Son of Man?

I once knew a girl;\\
We did a lot of work together.\\
We would chat on WhatsApp\\
And answer questions together.\\
I was mad and out of my wits\\
Over her and she had me for a ride.

I once knew a girl;\\
I felt so much peace being by her side.\\
We could have achieved things together.\\
Yes, we could have achieved a lot\\
But she betrayed me and mocked me.\\
She lied about me

And about my language.\\
She played games with my mind\\
And said that she loved it.\\
She even called me Baby\\
And I was furious.

She tried to make me\\
Into a lust puppet\\
Like another girl I came to despise.\\
I found myself asking,\\
What is wrong with this people?

You see, the girl I loved\\
Gave me a lot of sorrow,\\
Great afflictions\\
From the second year\\
And she loved and enjoyed every bit of it.\\
Talk of psychopathology\\
And psychopathy.

This one is like a satan for a human;\\
Such a shame to be with one.\\
She shall not profit anyone;\\
Thou knowest it that it is true.

We could have achieved a lot together.\\
She was even the one who encouraged me\\
In the early days to post my poems\\
And even to add a copyright symbol\\
So it could not be stolen by another.

Her friend even calls her kind\\
And I myself have seen her\\
Donate a hundred cedis to a mate in need\\
And I was there when she rejected my ten cedis\\
And returned it to me like a saint

And I was furious at myself for sinning\\
And went before the God of heaven\\
Who is great in compassion\\
And I taught myself knowledge\\
As I had heard from the scriptures ~
And learnt that the one who gives to the rich\\
Shall come to poverty.

Of a truth, the devils heard my cry;\\
They said they would fulfill scripture\\
And make me poor.\\
They said that they would ruin me\\
And make me miserable

So they came together\\
And decided to afflict me mentally.\\
They took me to the psychiatrist\\
And I received a formal diagnosis.\\
The doctor gave me my diagnosis\\
And medicine.

It was formal;\\
I had schizophrenia.\\
Now, you satanists out there,\\
I have made your work easier;\\
It should be easier now to defame me\\
Like you always do\\
And have done to Dr Rebecca Brown.

Satanists are fools;\\
They aren't half as intelligent as I am.\\
The most intelligent priest among them\\
Is as lame of wisdom as an ostrich\\
That buries her egg in the sand\\
And says it is a rock that shall not perish.

You satanists out there,\\
Wait for Heilel and not for me.\\
I am a grave disappointment\\
To the kingdom of Satan.\\
I do not profit the darkness\\
But Heilel will.\\
I am sure.

Next time, let's see if another lass\\
Or woman will come\\
And rob me of my peace.\\
All the losers are damned.\\
They shall not profit.

Give not thy strength to lasses\\
Neither let chickens rule thee.

Aphrodite is a cow who speaks chicken.\\
She is a leech and the firstborn of Baalzebub.\\
Satan is a dragon who speaks flies and buzzing.\\
Baalzebub is a leech who speaks duck.\\
Nisroch is a duck.

I was there at a conference,\\
A prayer conference actually.\\
I heard dogs barking\\
In the congregation.

Everyone heard dogs barking.\\
We were all schizophrenic\\
And hallucinating

Because the devils poured themselves\\
Out upon us and the death ones yielded.\\
No, the death ones actively did it.

That night, there was a heavy downpour\\
As though to answer the prayer of the priest.\\
The elements poured down water.\\
The rain poured down\\
Like streams out of the rock.

Once, there were thunderings;\\
The devil spoke in the thunder,\\
He said he had subjugated all powers;\\
He was mocking Hermes\\
As he called himself Lucifer.

God said, Ephraim is an unwise son.\\
Who is Ephraim?\\
Ephraim is Satan, the anti-INTJ\\
But Ephraim can also be Hermes\\
Or even Baalzebub.

I wonder why those who possess peace\\
Do not guard it with jealousy.\\
I wonder why no one cares about me.\\
I sit in my place;\\
I muse and I meditate.\\
I wonder why there is no one with me.

When Jesus was on the cross,\\
He called out,\\
Eli, Eli, lama sabachthani?\\
My God, my God, why have you forsaken me?

Pseudomic told me,\\
Never ask why,\\
Never ask why\\
But Pseudomic is a fool.\\
Surely, I can't heed his words.

Hmm, I had some questions for God.\\
Could Pseudomic be right,\\
The one who prays in toilets\\
As though he prays to Baalzebub,\\
The Yahoo and god of dung,\\
The lord of the fly?\\
That Baalzebub may well be Hermes also.

I had some questions for God.\\
Did Satan pay me a visit\\
To preach the message\\
That he is the god who draws near to me?\\
Is Satan mocking me like he mocks satanists?\\
Is he trying to call me a fool?

Hermes stood beside me.\\
I wrote that he stood behind me\\
And that he is my friend and strong tower,\\
That he is there with me\\
When the storms are raging\\
And that he fills me\\
When my strength is draining.

I wrote thus\\
Because, then, I thought that figure was Jesus;\\
I didn't know that it was Hermes.\\
I didn't know that he gave\\
Heaven and hell revelations to Christians.

This false Jesus\\
I saw leading me from Engineering Gate\\
Away from the direction of my hostel\\
As though to say he was with me\\
In my afflictions and felt my pain\\
And my disappointments.\\
Heck, you orchestrated them.

This false Jesus was on the left side,\\
Even on the left side of my bed\\
At the time when I slept\\
With my head away from the door.\\
You remember how I said Baal was on the right side.

Hermes asked me what I wanted;\\
He asked me like God asked Solomon;\\
These perverts have corrupted the name\\
Of the wisest man that ever walked the earth\\
And put his name on the abominable\\
Rite and religion of Masonry.

The Templars that despise the cross\\
And urinate on it like Bohemians\\
Are not satisfied but have returned\\
To provoke us to anger\\
With their villainy!

I did not hear Baal's voice openly harass me;\\
He maintained far more decorum\\
Than Satan, Hermes, Aphrodite and Baalzebub did.\\
You know in medicine,\\
You examine from the right side of the patient.

It is clear Hermes wanted to destroy my studies\\
Just as Enlil wanted to.\\
Thus, Satan's kingdom was partly divided\\
Like iron and clay that cannot mix,\\
Like nepheshim and ruachim that are divided.

Lucifer is Hermes\\
Not just Baalzebub.\\
Baalzebub is made of iron\\
And dwells in 335‰ light\\
But Hermes is made of steel\\
And is 535‰ light.

His star is Tophet,\\
Even the same Tophet\\
That is prepared for the kings of satanism.

Pseudomic kept asking me for money.\\
Buy bread for me; buy bread for me.\\
He was from a rich family too.\\
He is a spitting cobra not a leech.

He was trying to drain me of my resources.\\
He was loaded with greed.\\
He would not even return\\
The Waakye seller's change to her\\
Though I pointed it out to him.

He sought to discredit me\\
After the manner of satanists and Freemasons.\\
All they do is silence dissidents\\
Whether through defamation like satans\\
Or through cold-blooded murder.

So what is there in this cosmos?\\
Some are good and some are truly vile\\
But none can satisfy\\
Like a saint can.\\

Righteousness of character,\\
A perfect and zealous nature\\
Is to be priced above gold and rubies.\\
You should be zealous for holiness\\
After the manner of Melchizedek.

God has sworn and will not repent;\\
Michael shall surely become an el\\
And attain unto knowledge\\
Under the course of Melchizedek.

Melchizedek ruled over the Jebusites\\
And in his days there was peace\\
For he is the prince of peace.\\
He is Shiloh and Salem.

Gabriel, let me ask you.\\
Is Kabodel a male or a female?\\
Is Melchizedek male or female?\\
Melchizedek is the saint Kabodel,\\
The image of Shachar\\
And the sole saint beside Shachar\\
For more than one infinity infinitons.

Melchizedek is Illai\\
And Shachar is Elyon.\\
Shachar is God,

The doubly strong one\\
Who combines El with On.\\
He is made three times strong\\
And rules by his yad in the yod.

Heilel wants to be like Elyon,\\
He wants to be like the Most High.\\
The ben Yalal Shachar wants to yalal.\\
He will have a lot of sorrow.

Baalzebub wants to be the One.\\
She says, I am and there is none else.\\
She calls herself On.\\
She calls herself strong.

But thou art a weakling.\\
Thou shalt no more be called tender and delicate.\\
Thou shalt be like Samson.\\
They shall put out thine eyes.

Baalzebub shall go into perdition.\\
She shall fall and none shall deliver her.\\
She shall go down into the depths,\\
Even the depths of the pit.\\
Prepare a wildcard against her;\\
Prepare several wildcards that may afflict her.\\
I am in the number.

Do you know why Heilel rebels?\\
Do you know why Zuriel of earth rebels?\\
Do you know why the Tyrian king and prince rebel?\\
They rebel because they love the devils;

They are covenanted with the shedim in love;\\
They rebel because foolishness\\
Dictates so and they must oblige;\\
They lack wisdom.

Why do you think satanism\\
Is called the Brotherhood?\\
Why do you think they destroy so much life\\
And spill so much blood\\
And curse the earth and curse God?

Heilel cannot bear to remain faithful to a God\\
Who afflicts her own\\
And destroys the shedim\\
And humiliates Baalzebub.

Gabriel has bound Heilel,\\
Even Heilel's heart to the shedim\\
And she is become Satan's eye\\
And the wielder of Satan's authority.

Listen to me, O little lilies,\\
You who are excellent in form\\
And have been declared precious;\\
Listen to me, O lilies of the pond\\
For the wicked shall consume away.\\
They shall consume away standing.

Be ye meek and follow me.\\
Pick up your crosses and choose peace.\\
Pursue righteousness and be saintly.\\
Choose holiness and cling to it

For the saints shall rule.\\
They shall be the excellent in the cosmos.\\
They shall bear rule to the ages\\
Even world without end.

What do ye proclaim against me?\\
What does the assembly of the cruel\\
Devise against me?\\
They only consult to cast me down;\\
They are set in their ways.\\
They can never be like the meek lilies.

I will teach ye excellent things;\\
Sit down in the grass;\\
Fold your legs and listen;\\
Listen attentively to my words;\\
Hear the voice that distils in your ears

For my voice shall be pleasant;\\
It shall fall upon your ears\\
Like the sweetness of the rain\\
Or the light showers in spring.

It shall be like gold in the earth,\\
Like a precious diamond\\
That is worth dying for\\
And even better living for.

It shall be your health and life.\\
It shall deliver ye from darkness\\
And your souls from the flaming grave\\
And give ye hope and a future.

It shall establish your goings\\
And make your paths broad;\\
The narrow shall be enlarged.\\
Ye shall grow fat and discern peace.

Spread your wings and soar.\\
Look at the heights above.\\
Spread your wings and soar.\\
Lift up yourself and rise into the light.

Beauty is greatly to be desired.\\
Fear the Lord and be great.\\
Beauty is splendour;\\
If it fades, many do lament.

I can imagine a lass,\\
A beautiful lass.\\
Her hair swirls in the sunlight\\
On a bright new workday.

She is always happy;\\
Her brother drew in my book;\\
He drew a horse in my book\\
And I added his name below it.

Do you know Sariel,\\
One of the chief princes?\\
You know Michael\\
Who stands with and defends Gabriel\\
But do you know Sariel?

The chief princes are five;\\
They are Michael,\\
The linked spirit of Enoch,\\
Gabriel, Sariel and Samael.

Sariel of heaven is in charge of bliss;\\
Her codebase determines\\
How happy each person can be;\\
She is the bringer of bliss and joy.

Do you know beauty?\\
Have you seen Sariel of earth?\\
She is the most beautiful,\\
The most beautiful lass\\
I have ever set eyes on.

Truly, earth is tob.\\
The beauty of nature is glorious.\\
The green trees in the sunshine,\\
The snapping turtle\\
Crushing a watermelon,

Truly life is beautiful\\
And full of spectacular sights\\
And diverse beauties;\\
Each has its own glory.

Walk along the seashore.\\
Behold the flying fish.\\
Go close to a dolphin ~
Or make friends with an octopus.

Walk along the seashore.\\
Watch out for any crabs.\\
Just enjoy the fine breeze\\
And listen to the sound\\
Of the waves\\
As they crush on the seashore.

Truly life is full of life.\\
Have you seen a lass as resplendent,\\
Even as charming as my German Indian?\\
She never got to hear it from me\\
But, boy, was I moved by her beauty!

Truly life is gorgeous.\\
Kabodel is your king\\
And the sons of tsedek shall satisfy me;\\
They shall make me glad\\
More than wine the young men's heart.

Call out to your companions.\\
Bid them come and see righteousness.\\
Witness the works of the Lord:\\
What devastations and desolations\\
He has wrought in the earth.

He makes wars to cease\\
Unto the ends of the earth.\\
He breaks the bow\\
And cuts the spear in sunder.\\
He burns the chariot in the fire.

He makes the seed die\\
And brings up the young herb\\
And gives life in abundance.\\
He gives the command\\
And the foundations of the earth are laid.

Though earth be furnished a full body,\\
Yet Shinar's ziggurat shall not be finished;\\
It shall not be capped;\\
It shall not be built to the ceiling\\
Because we will destroy the works of Marduk.

Call the solemn assembly.\\
This time, those in charge of the city\\
Are not necessarily the seven spirits of God;\\
Everyone is called to the battle,\\
Even as many as shall respond to the Lord.

Come ye from far and near.\\
Say ye to the princess,\\
To the beautiful daughter of Zion,\\
Thy King and father cometh;\\
He rideth upon the holy earth that quakes;\\
He runs to the kill.

Thy father, O daughter,\\
Is a general;\\
He is the chiefest of ten thousand,\\
Even the chief in the cosmos.

Michael shall go before him;\\
The sun of righteousness\\
Shall shine from the east.\\
When the enemy shall pour in like a flood,\\
The holy spirit shall lift up the hedge against him;\\
The door shall be slammed in his face.

Come ye, come ye to the king.\\
The daughter of Tyre shall be there too.\\
She shall be preserved in the time of war.\\
She shall rejoice with thee, O Kabodel.

Come, O daughter,\\
Come, O beloved and elect of the King,\\
Her name is Mishchar;\\
She bears the insignia of Shachar.\\
She has his image.

The virgins her companions\\
That accompany her\\
Shall enter the King's presence with singing;\\
They shall sing and rejoice\\
And sorrow and mourning shall be stayed.

Forget your father and his house.\\
Come, join the king in his lair.\\
Enter into the craggy palace,\\
Come into the den\\
And be protected from the war without.

The spirit of understanding said to me,\\
The ENTP male declared to me and he said,\\
The ivory palace that thou seest\\
Is but a craggy den\\
For his spirit shall live as a lion.

Upon mount Zion shall be deliverance;\\
There shall be holiness\\
And the Lord shall show us mercy

For strong is he that watches over our souls\\
To save and to strengthen them.\\
His name is the Lord\\
And his remembrance is eternal,\\
Even to the ages, world without end.

Know that in that day, Heilel shall live;\\
The ben Shachar shall live and not die\\
For great shall be the Lord\\
And his peace and covering shall save.

Spread thy wings, O cherub,\\
Fly thee to the west.\\
Set up your throne in the great land.\\
Rule thou over Europe.

Thus it shall be:\\
Heilel shall rule over Europe.\\
The daughter of Tyre,\\
The daughter of Europa\\
Shall ascend to Europe's throne and reign.

Glory, O glory to the righteous.\\
Everyone whose name is in the book,\\
Even everyone lacking the death trait\\
Shall be saved and preserved.

At that time\\
Shall the sleeping Saint be aroused.\\
He shall rise up and stand\\
Executing the judgment of a saint.

Everyone shall be saved,\\
Even everyone who shall be found\\
Written in Kabodel,\\
Even everyone in the book of life.

But you say,\\
How shall Heilel live?\\
Heilel shall live for she is a princess,\\
A lady and daughter of the king;\\
She shall live to the King's glory.

The elect shall come to Jerusalem.\\
There they shall encamp against us\\
And there we shall destroy them\\
And give up their bodies to the rot.

The feeble among the elect\\
Shall have as it were the strength of David\\
And David, even the chief, the strength of God.\\
There, they shall batter the nations that offend.

War is decreed upon the nations.\\
The end is drawing near\\
And the nations shall know their shame\\
And the people their glory that is marred.

Show decorum and honour.\\
Honour the Lord and resist him not.\\
Do not strive with God\\
Though Jacob wrestles Peniel

For Peniel shall bless\\
And Israel shall be blessed\\
But the angel of the LORD shall curse\\
And Meroz shall be cursed.

Rejoice, O ye saints with his people.\\
Your brethren that thrust you out,\\
Your nations that pursued you\\
Shall fall down slain before you\\
As in the day of Esther in Shushan.

They encamped against the camp of saints.\\
The fire of God came down.\\
It consumed them with their hosts\\
As in the day of Sodom and Gomorrah.

They perished in the fire.\\
They fell down slain.\\
The sword shall devour the rest.\\
Do not give them all to the fire.

Blessed is the King\\
Who comes in the name of the Lord.\\
Blessed is the Lord\\
Who alone reigneth over all\\
And is exalted above all.

Hear ye the words of Moses\\
How he said that the Lord,\\
Even God Most High is a man of war.\\
He created not the universe in vain.\\
He said not to worship in vain.

The idols of the nations shall fear.\\
The idols of gold and silver,\\
The idols of stone and wood,\\
All these shall be thrown away.

Man shall see and know and understand\\
That salvation does not come from Egypt.\\
The pyramids of Egypt shall not save.\\
Those who put their trust in Satan

And worship the goddess\\
Shall be put to the worst before God;\\
Their destruction comes burning like an oven.\\
In that day, the law of the ra'ah shall be broken.

They too shall feel pain like us.\\
They shall die in pain\\
And begin to savour of their wickedness\\
And perish; stumbling, they shall fall.

So the righteous shall be with God.\\
They shall be on the Lord's side\\
In whatsoever country they find themselves.\\
They shall bind princes\\
And execute upon them the judgments written.

I will mention the lovingkindnesses of the Lord\\
Which he has poured out upon us in his love.\\
He holds us in his hands\\
And calls us his children.\\
He numbers our days to shalom.\\
All of us shall dwell in Shiloh.

\chapter{Vanity}\label{vanity}

Vanity of vanities;\\
All is vanity.

When the viper bites the heels of my horse,\\
What shall happen to me or to it?\\
I shall stand up after falling backward\\
And crush its head with my strong boots.

I have waited for thy Yeshuah, O God!

Of a truth, God has purposed it;\\
He took counsel with no one;\\
He consulted with none.\\
He himself hath purposed it\\
To do according to his pleasure.

God hath determined to stain the glory of Ephraim\\
And to mar the haughtiness of Hermes\\
And to disgrace the treachery of the rebel\\
That he might instil fear in his enemies\\
To whom he gives the breath of life.

God has determined to dishonour Hermes;\\
He will destroy and cut him off\\
That he shall be no priest in the room of holiness\\
Therefore hath Hermes sinned so vilely\\
And stooped so low and fallen so hard,

Therefore did he not fear\\
But strengthened himself in sin\\
And latched onto the train\\
And attacked me early.\\
His judgment shall not be stayed.

I have waited for thy salvation, O God.

This shall be the judgment of the wicked,\\
Of all the devils that have fought against me\\
And desolated me,\\
Chiefly, Satan, Hermes,\\
Baalzebub and Aphrodite,

This shall be the judgment of Satan\\
And his angels\\
In the day that the LORD\\
Shall break their arms\\
And destroy them for their folly,

This shall be their judgment:\\
They shall be blind\\
And not see the sun;\\
They shall be mute, even dumb;\\
They shall not be able to read minds\\
Just as we have long believed about them;

Moreover, they shall have null feeling\\
Like those who are dead\\
Who feel neither pain nor pleasure;\\
They shall be struck out of Sariel's book,\\
Even out of the benefits of Sariel of heaven.

These judgments shall be executed by God,\\
Even by God the Saint.\\
Not by earthly might nor power\\
But by the spirit of God\\
Shall the iniquity of the land be removed in one day.

Shiva and Satan\\
Shall see darkness and nullness,\\
Even emptiness;\\
They shall be blind forever\\
For strong is the saint that judges them.

This is vanity and vexation of spirit;\\
A saint saves while an el can do nothing.\\
Araphel and Qerenel behold from above\\
And yet there is no salvation in them\\
To deliver me from my adversaries.

God considers carefully\\
And wonders why there is no one\\
To deliver and no arm to save\\
And no one to send for an apostle and deliverer.\\
Thus, he puts on zeal for a cloak\\
And his wrath, it sustains him.

He will surely do it;\\
He will put out the remembrance of Satan\\
From under the heavens;\\
He will take away the bliss of the death ones

And satisfy the judgment\\
And get him honour\\
And ascend to the glory;

He shall loose\\
The shoes of iron and brass\\
From off my feet\\
And set me at ease\\
For there shall be no Asherah or viper to crush.

The desire of the nations shall come;\\
All creation shall rejoice\\
That the Assyrian is broken in my land\\
And that the wicked ones are shattered;\\
Surely, Marduk shall not be pardoned.

Tell me, what meaneth this war\\
That the adversary hath dealt so bitterly?\\
He hath dealt without shame;\\
He hath offended without holding back;\\
Ephraim provoked me most bitterly;

His blood shall be left upon him;\\
He shall taste of all four:\\
Ira'ah, itob, iblis and ichesed.\\
He shall eat and be full of the judgment of God.

The enemy, the devil, cometh not\\
But to kill, to steal and to destroy.\\
He hated the earth with bitter hate\\
And loathed Adam who was fashioned\\
Out of the earth.

Together with Baalzebub,\\
Satan, under Marduk's direction,\\
Stole our bliss\\
Which was a tenth of the heavenly bliss,\\
A tenth of the earth's bliss,\\
A tenth of the bliss of the stars,\\
A tenth of the shalom shamaim

And replaced it with dumbness,\\
Stupidity and pain and suffering.\\
They made slaves out of us\\
And now they return unsatisfied\\
To take away the rest of our peace\\
And to give us hell.

Baal says they trade in souls.\\
Their hatred is great.\\
They hate us;\\
They cannot fathom the love of God for us

And they keep pondering and asking themselves,\\
What is man that God is so mindful of him?\\
They visit us and come in place of God\\
To vaunt themselves as God

And to lash out with hell.\\
They shall have hell in retribution\\
For the day of vengeance is in God's heart.\\
They shall surely not escape,\\
Even every one of them.

Their destruction shall be swift.\\
Their judgment shall come in one day.\\
They shall be bounced out of bliss\\
And fall into the darkness\\
Wherein they shall be chained.

Bind them, O God\\
With your great chain.\\
Lay hold of the dragon\\
And bind him up\\
That he, mute and blind,\\
May deceive the nations no more.

The brides of Hermes shall be stunned;\\
They shall be left confounded\\
When they cease to hear his sweet voice\\
And his deceptions.\\
Lots of hearts shall be broken\\
And blood will distil as rainwater.

To me belongs vengeance;\\
The footsteps of the vile\\
Shall slide in due time\\
And the things that shall befall them make haste.

Rejoice, O earth with the elect\\
For the Lord will reign\\
And the iniquity and vexation shall cease\\
And the elect shall delight in holiness.

This is but a matter of zeal;\\
It is a controversy of motivation\\
For even Samael takes on Baalzebub\\
And humiliates her,\\
Even Samael destined\\
To destroy the messenger of Satan,\\
That great thorn in the flesh.

Blindness is happened to all\\
Therefore there was no one to save.\\
The mighty could do nothing.\\
The lion and the cherub just sat in their places.\\
The mighty Qerenel in whom are all things\\
Could not move a finger against Satan.

We all grope at noonday\\
As in the thick darkness.\\
Araphel, where is your strength?\\
Gabriel, wilt thou win a war\\
With butterfly wings?

Satan gave a command;\\
He said, Fight against none but Saviour.\\
Wherever he shall go, there go ~
And give him no rest\\
Whether day or night\\
Till we have our prize.

Give them desolation, O God.\\
Let them be in desolate places as the dead.\\
They came for desolation.\\
They came to waste me.

They did not come to profit themselves.\\
They came, like Aphrodite, for vanity.\\
They came for mockery,\\
To steal my honour and sanity\\
And to destroy me.

They came to defame me;\\
They came for shame.\\
They came for vanity.\\
They love to slaughter.

They love to harass;\\
It shall not profit them.\\
They shall not be enriched.\\
They shall be impoverished.\\
They shall not prosper.

They came to waste me,\\
To turn my honour into shame,\\
To turn my knowledge into foolishness,\\
To corrupt my mental capacity\\
And to stop me from learning.

Pseudomic and the vile,\\
The fools that forwarded my affliction,\\
Said among themselves continually ~
And they said it in my hearing,\\
He is still learning.

They said it;\\
Veredel was in the conspiracy.\\
Their ways are ways of villainy;\\
They are most bitter;\\
There is no sweetness in them.

God will save me.\\
O, taste and see that the Lord is good.\\
He gives salvation to his son\\
And rebukes the company of scorners.

He destroys the proud and haughty,\\
Even the proud that exalt themselves\\
Against me and lift up the shoulder;\\
They are swatted as flies.

Promotion comes from God\\
And the strength of salvation is his work.\\
He puts down one and sets up another.\\
He makes Michael second\\
And sets Yirel above him.\\
In God's hand is the power to rule\\
And the glory to appoint.

So, Michael remains a ben Mishchar forever\\
But Heilel perishes, even Heilel,\\
The son of perdition and destruction.\\
Heilel, the brilliant and shining one\\
Who shines with 666‰ light,\\
Shall be replaced with an even more brilliant one;

Yirel, the dove that descended upon Jesus\\
And strengthened him in the fear of the LORD,\\
Shall be Heilel's replacement\\
For she is Shachar's beloved child\\
In whom God is well-pleased\\
And the bath Shachar of the appointment.

Heilel shall howl in pain like Enlil.\\
I'm thinking along the lines of 980‰ light,\\
About 140 × 7 in light proportion.\\
So, Yirel shall destroy Heilel with her shining\\
And take him down with the light of her brightness.

So, Yirel, the seventh spirit of God,\\
Is the Platinum Chief\\
And the Lord or Lady of the Assembly;\\
She is Tyr and her nemesis is Enlil,\\
The Death Chief.

Michael does not know what to do.\\
Maybe, he is waiting for a command,\\
A commandment that will never come.\\
He cannot be first ruler\\
Because he needs direction;\\
He must always be guided.

Elijah is scared of death;\\
He will not repeat Earth's sufferings.\\
Heaven is too sweet;\\
Asherah, the Hell, has guaranteed its peace.

Elijah will just mind his business
And pretend everything is ok;
He cannot bear to draw attention
To himself or to announce his presence.

He would rather choose life\\
Than die a fool like me.\\
Once, he humiliated Baal\\
But will proceed no further.

He is scared of death.\\
He wants to live\\
Like I told myself in my childhood\\
And said I would never go to Jerusalem\\
For fear of being killed\\
When I woke up from my dream.

The devils are in their element;\\
The vile ones keep touting Satan\\
And swearing by a force\\
They have no knowledge of;

They say, He has favoured our undertakings;\\
Annuit coeptis.\\
Animdife is laughing at them;\\
A little kid from an unnamed village\\
Who broke out of lockdown is mocking.

What does Animdife mean?\\
It means house of the chiefs\\
Or house of those who lead in front\\
Or house of those who occupy the front seats;\\
Wisdom told me I was favoured;\\
I'm still waiting for my turn to step forward.

The devil, that leader of the cruel,\\
Came after me and attacked.\\
The traducer said, I lead\\
And I said, Like Baalzebub,\\
You have found your match.

The earth is the Lord's\\
And the fullness thereof,\\
The world and they that dwell in it.\\
Marvel not at the dragon.\\
He is a thief.

He does not rule the earth;\\
He rules illegally\\
As a thief\\
Till his cup runs out\\
And he goes to prison.\\
He shall have eternal shame.

All of them that serve idols\\
And trust in iguanas that shall not live\\
And decorate gods of clay\\
And say unto them, Arise and kill,\\
All of them shall go into perdition.

Do not pour libation.\\
Pray not to the ancestors.\\
Do not put your trust in vain idols\\
Neither make abominations your god.

They are works of stupidity;\\
They have no breath in them;\\
They have no spirit\\
And they have no honour.

Enlil is but a vexation;\\
He has no love;\\
His natural senses are dulled.\\
He loveth to oppress.

Read about him;\\
He is covenanted with fools\\
For that he himself is a fool,\\
He cannot but pursue folly.

The satanists that serve Satan\\
And worship the goddess,\\
That write the name of Jehovah\\
And use it in their rituals\\
And desecrate the Most Holy,

The witches of Bohemia,\\
Those effeminate idiots\\
That drink alcohol\\
And worship Moloch

Shall pee their hearts out\\
Yet shall their sin remain.\\
When their blood shall be required,\\
Then let the Satan they worship\\
Come to their rescue.\\
How pleasant their deaths shall be!

Go into the caves.\\
Bid the rocks fall on ye\\
And hide ye from the wrath of the King\\
And the fierce anger of the Lamb\\
As he roareth from Zion.

They build dynasties\\
And afflict their progeny.\\
They curse their seed\\
And add incest to incest.

They shall not profit;\\
They shall not see the light\\
Because in their boast of illumination,\\
They have sinned the sin of Pharaoh\\
And dug their graves\\
In which they shall not be buried.

They shall not be mourned.\\
They shall not be gathered.\\
We have given their bodies\\
To be scattered as dung\\
Upon the face of the earth\\
They have profaned and insulted.

Ye fools that organise parties\\
And send letters sealed in gold\\
And written in fancy letters\\
To the young and budding,\\
To the up and coming

And bring them in\\
And put masks on their faces\\
And say to them,

Fill your appetites,\\
Eat voluptuously to your lusts\\
And defile yourselves;\\
Make yourselves vile;

Defile yourselves to hell\\
And make Baalzebub happy,\\
Even Asherah of the pervert groves,\\
For the sin was not cancelled\\
And there is no redemption,

Ye fools that persecute souls\\
And are skillful to harass and destroy\\
Like your father the devil\\
And like Asherah your father,

That say to your emissaries\\
And hitmen and henchmen,\\
Go and strike,\\
Strike and destroy that fool,

Ye shall be found fools\\
And your rituals\\
And your sex magic\\
And the prescriptions of Lucifer\\
And of your pervert priests of the Brotherhood

Shall not deliver ye\\
For ye shall be found fools\\
And found fools again\\
And found fools after that.\\
The greatness of your folly\\
Shall never be assuaged.

They pursue Eastern mysticism.\\
They chase after Kundalini\\
And immerse themselves in sensual Tantra;\\
Their wine is the poison of dragons;\\
Their honour is to be defiled.

Baalzebub wants to be defiled.\\
No, she wants to defile.\\
That's why she is the father\\
And Satan as Santana is the mother.\\
Baalzebub bows down to no one.

The fools shall come down together,\\
Each receiving the harassment due him;\\
They shall fall as lead into the ocean;\\
They shall sink and be found no more.\\
They shall not rise;\\
Affliction shall not arise a second time.

Go to, learn from the ants;\\
They are strong to labour\\
Not strong to drink liquor\\
Or to partake in foolishness.

A little child shall rebuke ancients;\\
A learned one shall insult the intelligence\\
Of the haughty and proud\\
For they shall come down from their seats,\\
All of them slain as Agag

And the noise of the viol,\\
The celebration of winter\\
And the worship of the sun in the dark season\\
Shall cease and everywhere\\
Mortals shall acknowledge their mortality.

The God of heaven shall reign;\\
His cherub, the cherub of Michael\\
That divided the sea\\
With the blast of his nostrils

And demonstrated his power\\
Over the leviathan\\
Shall destroy them\\
With the breath of his mouth.

Behold the sword from the Lord's mouth.\\
It proceeds double-edged\\
Whirling around and turning;\\
It proceeds out to the kill.

Like the sharpness of Isaiah's sword,\\
None shall escape its edge.\\
It shall be bathed in the heavens,\\
Up above where Satan dwells\\
And come down upon earth to slaughter.

Out of the Most High\\
Proceeds both good and evil.\\
He shall surely execute the wrath\\
And not pity.\\
He shall not spare.

He has determined it\\
And he will do it.\\
He shall put Asherah to shame\\
And give her bitterness for bliss,\\
Shame and a burning heart for joy.

Assemble ye,\\
Come ye together. ~
Stand in the place of judgment.\\
Let the books be opened.\\
This shall not be vanity.

We shall put an end to vanity.\\
It is the last dance.\\
Shiva shall dance to her death.\\
She shall drink her own blood.\\
She shall not have the Baptist's head.

They only love lies.\\
They love sweet talk.\\
They love to be deluded and deceived,\\
To believe that judgment will never come\\
Because the Lord can do nothing.

They always want to please themselves\\
And Baalzebub, the father of their lusts.\\
They love hatred and the hot, boiling blood\\
But are as cold as the Serbian winter\\
And cannot withstand the furnace and fire.

Against whom do they lift themselves up?\\
Against whom do they plot\\
With their square and compasses?\\
They shall be slain, all of them.

Iniquity shall not save,\\
No, not today nor on any other day henceforth.\\
The alliance of the wicked with death\\
Shall be broken and shattered.

Will you shoot me from behind?\\
Will you backstab me?\\
Will Cain stab his brother in the back?\\
Will Baalzebub stand and slander Michael?

These ones act in an underhanded manner.\\
Have you coals of fire to put in my hands?\\
Can you touch my lips with a coal of fire?\\
Can you draw near to me?

When the wicked prosper,\\
Then the heart of the saint is grieved.\\
The saint is there for one reason:\\
To destroy the works of the devil;\\
He will put out the light of Baalzebub\\
And trouble sinners\\
Till they are shaken out of the earth.

You have to be born a saint to be it;\\
You cannot be made a saint;\\
It is too sacred an order for another\\
To ascend to via any means.

Marduk shall die;\\
He shall not deliver Inanna;\\
He cannot salvage the soul of Baalzebub\\
Nor fight for Aphrodite.

He and Enlil shall surely envy their enemy\\
And both shall be as the darkness\\
In the room\\
That says, I am blind\\
And his fellow shall say,\\
What is he thinking?

The screech owl and Lilith\\
That Baalzebub is\\
Shall look for her mate\\
And find him not.

She shall long for Satan\\
And be distressed.\\
She shall not be comforted\\
Like foolish Judah with Tamar.\\
She shall believe Nanna is with her

But it shall only bring vexation\\
And a frustrated longing\\
That cannot be fulfilled\\
According to the law of Nanna.

Many shall fly upon cherubim.\\
They shall fly to the kill.\\
The dead shall die\\
By the light of the elect;\\
They shall consume away at the brightness\\
With Yirel leading the charge.

Where is Lucifer that may save?\\
Is he not also light\\
Or has he deceived the seducible,\\
Even the gullible and deluded?

They shall stumble and fall,\\
Every one of them\\
Drinking vinegar\\
And being comforted with gall.\\
Their bread shall be tears and sorrows.

Ask the green herb.\\
Ask the green grass.\\
Ask the lilies of the pond\\
And the mild and gentle vine,

Ask and they will tell you,\\
None of these things shall fail\\
For the feller shall be cut down\\
And he that came up to us\\
And destroyed our fine branches;

He shall be uprooted\\
That marred our glory\\
And led us astray;\\
He shall dwell in the depths\\
Of the lonesome grave in solitude.

So what shall we say\\
To these things\\
But that if God is for us,\\
Who can be against us?

Who is he that seeks my blood?\\
Who wants me dead?\\
Who cooked my vexations\\
And implements them?

Who stands against me?\\
Who is my adversary?\\
Who is my enemy?\\
Who says I shall not prosper?

Who will come up to me\\
Being my enemy wrongfully?\\
Who has despised me when I offended not\\
But that he could not tolerate the innocent?

That soul shall go to perdition;\\
His grave is a grave that is not dug\\
For it is not in the earth;\\
He shall go to destruction;\\
None shall restore him like Nebuchadnezzar.

Sing, O ye nations,\\
Sing, O ye peoples,\\
Both far and near,\\
Ye of the islands and far continents.

God shall come.\\
Thy God shall return.\\
His work is with him\\
And his reward before him.

He shall smite the ends of the earth\\
And give grace and glory.\\
He shall give life and breath\\
And all that hear shall listen and obey.

Heilel wants to be like Elyon.\\
The INTP wants to be like the INTJ.\\
Baalzebub called out to me,\\
She said, Saviour, keep typing.\\
Baalzebub, am I feeding you knowledge\\
Before your death?

Gabriel is Daniel's Lord.\\
He is a gibor like Kabodel.\\
Kabodel abides forever.

As a chief prince,\\
Gabriel's death would be most desirable\\
To the lords of darkness\\
Who rule over the perversions\\
Of this our world.

The only saint Kabodel\\
Who is co-saint with Shachar\\
Has been alive since infinity past,\\
Since the genesis of the first universe.

Araphel is Wisdom\\
And Qerenel is Understanding.\\
They are the King's delight.\\
Qerenel has geburah.

Gabriel is the one who says\\
Che sara sara.\\
What will be will be, he says.\\
He is an ardent believer\\
In predetermination.

Each one shall receive of his lot\\
And stand in his allotted place\\
Even if mine is to be harassed by fools\\
With Gabriel standing behind me\\
With butterfly wings doing nothing.

Asherah is still calling out to me.\\
She is mentioning my name\\
And saying she hates me.\\
She wants blood\\
And Marduk responds.

Go and sleep Marduk;\\
It is vanity to stay awake.\\
What for? Why do you open your eyes?\\
As in the garden, you shall perish!

Baalzebub is twice as rebellious as Satan\\
For rebellion is as the sin of witchcraft\\
And the enchantress will not stop;\\
She will not stop experimenting.\\
She is consumed with the judgments of Heilel.

She calls herself the roomy one;\\
She is the envious and silly one\\
Who is full of jealousy\\
And purchases souls as a father\\
Unto herself and to her son and husband, Satan.

Asherah wants Mammon,\\
The spacious one.

She will give Armageddon to Satan.\\
Satan shall stand\\
At the base of Har-Megiddon.

But, Satan calls himself Gaia.\\
He declares to all that Asherah is a friend-foe,\\
A confidant-rival, a benefactor-nemesis\\
Whom he would have smitten in the end

If his kingdom were established.\\
She is a thorn in his flesh\\
Like Joab was to David the king\\
Who declared that the sons of Zeruiah\\
Were too strong for him.

Asherah, that is, Baalzebub,\\
Is the personification of the sexual act.\\
She is the antichrist\\
And the rival of the spirit of righteousness.

Her deeds can only be done\\
In a body encoded by Mammon.\\
Paul declares to himself\\
That he shall never stoop\\
To bow down to the foolishness of Asherah.

Even those who escape the evil ayin\\
Are caught in Asherah's net.\\
Hermes fell in and, boy,\\
Did he fall in so hard!

I look at those who say\\
God commanded us to be fruitful\\
And say, Look at these murderers;\\
They wouldn't even sympathise\\
With the pains of their children.\\
There is no wisdom in them.

Asherah could not sing\\
To Michael and to God\\
When the earth's body was created\\
Because it was a body of righteousness\\
And she envied his creativity.

The sinners are simple creatures;\\
The foolish have not much intelligence\\
And understanding\\
And they hate to witness brilliance.

Asherah also slanders her own mother's son.\\
She consents with a thief and adulterer\\
And hast been partaker with aliens.

She slanders Michael\\
And blasphemes.\\
She calls herself the Lady. She is Freyja.\\
She shall shut her mouth.\\
We will shut it for her.

With Michael, we shall waste Freemasonry\\
And shake the people out of the earth\\
And we shall prosper by the four horns\\
Of the cherub and of the altar\\
And by the rhinoceros of the unicorn.

Everyone who chooses holiness\\
Becomes the target of Asherah\\
And Aphrodite the great.\\
These ones harass and don't stop.\\
There's no wisdom in them.

Everyone who loves Asherah\\
Hates her in the end.\\
She is as odious as a toad;\\
Her end is bitterness and torment.\\
She shall live peace-free

Like the odious\\
Marduk, Heilel and Zuriel of earth\\
Who spit out frogs\\
And send their uncleanness\\
Throughout the world of the damned.

If Asherah and Aphrodite's clothes are their skins,\\
Then Satan would have stripped them off.\\
He would have flayed them,\\
Even made their flesh bare and naked\\
And grilled their insides to feed himself\\
As the last man standing before dying of hunger.

The bringer of sexuality,\\
Even the bringer of the sexual act,\\
Can never be first.\\
She shall always be subordinate.

The female shall not rule\\
Because before her,\\
The sexual act did not exist\\
And the spirit of righteousness ~
Was not so vexed as it is this day.

The agony of Asherah\\
Is that she calls herself chief and first.\\
She says, I am and there is no one else.\\
She shall not prosper.\\
She shall not prevail.

None can stir up hate and jealousy like she does.\\
None can offend like Asherah.\\
None can provoke to jealousy like her.\\
None can evoke a storm with rage like Baalzebub.

I could not defer\\
My programme of instruction till she came.\\
I could not experience the worst year ever yet\\
Till Asherah did her campaign\\
And took over from Aphrodite.

None will experience\\
Prolonged devastation and wasting,\\
Even desolation and absence of joy\\
Like the abominable Asherah\\
And Satan and Hermes.

One of the major differences\\
Between Satan and me\\
Is that my hate comes with a legal reason\\
While Satan's hate is with an illegal reason.

The shedim have been probing God.\\
They have been searching God\\
Like searching spirits\\
And illegal entities

And when they find nothing,\\
Then they declare,\\
Is there knowledge in the Most High\\
And does the King have any understanding?

The light encodes nothing;\\
It is but raw power.\\
The light encodes nothing\\
So they think God to be null.

They think him to be some force\\
That they can harness and manipulate\\
And make their slave\\
Or reprogram and repurpose\\
To serve their purposes.

Go and hijack the unicorn\\
And let him abide by thy crib.\\
Put fetters upon his legs\\
Like Aphrodite attempts in her foolishness\\
When she is proudly declaring herself Father.

Put a yoke upon his neck\\
And let him plough thy fields\\
With his companion.

Thou shalt not prosper\\
Neither shall sinners prevail.\\
The God who forms knowledge\\
Shall cut sinners out of it.

Do not listen to the wild lies\\
And vanities of the shedim\\
Which they fabricate\\
And conjure up in their dreams\\
And dionysus frenzies.

Their dreams are vain\\
Which are as a puff of air\\
Which the wolf blows\\
Against a wall of brick and mortar.\\
He shall huff and puff in vain.

See, nothing is vain.\\
Nothing ever happens without design.\\
God oversees all things.\\
He makes all things\\
Beautiful in his time.

Thou shall return and know\\
And discern between righteousness and sin,\\
Between good and evil,\\
Between he that serveth God\\
And he that serveth his own lusts.

God tests no one.\\
He does not tempt us.\\
Remember how his angel\\
Was once referred to\\
As standing in Balaam's way\\
As a Satan?

God tempts no one\\
Because he knows all things\\
But to prove his servants,\\
Michael does tempt persons\\
As he tested Abraham\\
In the matter of Isaac.

He proved Abraham,\\
Even Abraham's loyalty to God;\\
He found Abraham faithful to him,\\
A servant that could be trusted

For Michael seeks faithful servants;\\
He seeks loyalists being an Fi dominant\\
And they that are with him\\
Are called and chosen and faithful.

He blessed Abraham\\
And made him father.\\
He blessed him in God's name,\\
Even in the name of the LORD.

In Satan's codebase,\\
There is a chasm\\
Between the amount of pain\\
The elect experience\\
Compared to the damned.

The odinits of the damned\\
Where Satan is\\
Are in the tens and hundreds\\
While the odinits of the elect\\
Are in the ones or zero.

I still do not know\\
If any of the elect crosses one odinit.\\
God himself does one odinit\\
And Michael and his Shulamite ~
And the latter's brides do zero.

We do not call Satan Odin for nothing.\\
He appoints himself many sufferings\\
And those he loves who are with him\\
Are with him in the blazing furnace\\
Which is the light of tobs.

Mammon\\
Is the mammon of unrighteousness\\
While Zion and Armageddon\\
Are the mammon of righteousness.

Mammon encodes all matter\\
And all wealth and all bodies\\
That are considered ritually questionable\\
Or even unclean or impure

While Zion and Armageddon\\
Provide the definitions\\
For all matter, wealth and all bodies\\
That are considered ritually pure\\
And clean and holy.

Light entities which are all tob,\\
Unlike the ra and ra'ah\\
Which are darkness entities,\\
Do not encode any knowledge\\
And thus are not indexed by the elim.

What bodies does Mammon encode?\\
Ritually questionable bodies\\
Including all bodies of flesh and blood\\
That have an orifice or cavity or body fluids\\
Including the bodies of Adam and Eve\\
And of Jesus and Paul and myself\\
And of every human or animal\\
That has ever lived.

Likewise all other sexual bodies\\
Including trees, a symbol of fertility,\\
And all bodies that depend on external agents to live\\
Including viruses and bacteria and fungi\\
Because they require nutrition\\
Are encoded by Mammon.

All living bodies that are not flesh and blood\\
And that are asexual in appearance\\
Are encoded by Zion\\
And this includes all the bodies in heaven\\
Whether animate or inanimate\\
Including the bodies of Mammon\\
And Armageddon themselves.

The heavenly bodies\\
Including the stars and planets\\
And meteors and meteorites,\\
Comets and the sun and moon\\
And the shamaim and raqia\\
And the maim and Qerenel\\
All have their bodies encoded by\\
Zion.

The golden earthly body of Shadel\\
Which the false prophet\\
Commands to be made for her\\
Is also considered ritually pure\\
As it is asexual and not of flesh and blood\\
And is encoded by Zion.

If the body is made of flesh but ritually pure\\
And thus asexual and shut up\\
So that it lacks body fluids\\
And body cavities and orifices\\
Like the bodies we shall have\\
In the regeneration when Christ returns,\\
Then it is encoded by Armageddon.

So you see,\\
Armageddon is a prince among princes,\\
A distinguished one and very wealthy\\
And he decides the fate of many\\
Together with Zion and Mammon his brothers.

Armageddon shall increase in honour\\
While Mammon shall decrease\\
And become the lowly Ebyon\\
Among the nations and continents.

Boast not about your riches,\\
O great Mammon of heaven.\\
Seek true wealth\\
Like the gold of Shemesh\\
That thy poverty\\
Like nakedness in the cold winter street\\
Become not thy undoing and death.

Mammon is the angel of Laodicea.\\
He is quite cold for heaven\\
Though burning like an oven.\\
He registers a temperature of 1,000F\\
While the rest score at the normal 10,000F.\\
Armageddon is ten times hotter than normal.

That's like the temperature\\
Of a bluish O-type star\\
Which stars are the hottest,\\
Most massive and brightest stars.

You get the idea of what righteousness\\
Looks like or feels like.\\
I'm sure Apollyon understands.\\
Abaddon nods his head.\\
He gets it; he understands.

Zeus, that is, Baalzebub\\
Is out there to tame the wild.\\
She can only be the wild one here.\\
She wants to tame the lightning bolt,\\
That blazing and flashing lightning bolt\\
That Armageddon is.

She was successful with Satan\\
Under Marduk's counsel.\\
Now, she eyes Armageddon ~
And she spies me with her ayin

But I am meek and gentle.\\
I will not offend.\\
I have never cut the throat of a chicken\\
And I keep touting epidural analgesia\\
For labouring women.

Kabodel was there in infinity past.\\
He gave life to Michael in the beginning,\\
At time t=0s\\
While Shachar gave life to Heilel.

Their appearance marked\\
The beginning of Genesis\\
And the two are the firstborn twins\\
Of creation.

Michael was given the pathway\\
Of work and creation\\
While Shachar gave Heilel\\
The pathway of rest and observation.

Why did Kabodel join me in the fall?\\
Why did she come down?\\
Well, when a saint moves left,\\
The rest of them follow.

With one spirit like Ezekiel's cherubim,\\
They go wherever one goes.\\
If one goes for the kill,\\
The rest follow.

If one withdraws the hand,\\
The rest also withdraw theirs;\\
These are the most unified group\\
In the whole cosmos\\
Like some group of special force.

Mishchar retains a thousand units of ra;\\
The ra is for hatred for iniquity\\
And the nine thousand tobs to love righteousness.\\
Mishchar is Melchizedek receiving tithes\\
Even in tob counts.

You can't be a saint and not hate Satan.\\
You must hate and execute wrath\\
On the adversary, even the oyeb.

God is a saint first\\
And a tob and el second.\\
It should be clear by now\\
That when God works,\\
He works through another.

Whether he is creating through Michael\\
Or through the sea or earth,\\
He almost always has an intermediary,\\
A front person to execute for him.

Mishchar is the Word of God\\
Who was with God in the beginning.\\
Out of her womb comes life.\\
She commands her son Michael\\
And he creates and fashions things.

Qerenel is the geburah\\
Who is the delight of Mishchar, the gibor.\\
She is always in his presence,\\
The Understanding that was with him\\
From infinity past,\\
Who was there when Mishchar\\
Gave the decrees of creation.

So, Qerenel is the angel of the presence\\
Who saves the elect\\
By giving the command for Samael\\
And the host to destroy the rebels.

She is also the master craftswoman\\
With Araphel and the two\\
Are the excellent or large and noble ones\\
Who guided Michael on how\\
To pattern and design creation\\
With each command that Mishchar gave.

All things were created for Mishchar.\\
He is the book of life.\\
All things that live as it is today\\
Live because he has commanded it.

God is the Commander-in-Chief standing\\
In the midst of his special forces.\\
He sets a little child\\
In the midst of lions and dogs,\\
In the midst of caracals and bears;\\
He shall excavate the substance\\
Out of Baalpeor with the woodpecker.

In the Genesis story of creation,\\
God is the Supreme Commander,\\
Mishchar is the General,\\
Araphel and Qerenel,\\
The Wisdom and the Understanding,\\
Are the Colonels\\
And Michael and Heilel\\
Are the Command Sergeant Majors.

Vanity of vanities,\\
Perchance the greatest vanity\\
Is that it would be found out in the end\\
That nothing and no work of God\\
Is in vain or empty.

The works of God are full;\\
They are complete for their purpose\\
Even if they appear to waver;\\
Each fulfills their role to satisfaction.

The Lord directs each\\
Including the rebellious\\
And the captive\\
And the vile and the dishonourable.

He will put each in his place\\
And fashion the form appropriate for each.\\
The screech owl has her place\\
And the deceiver also has his place.

Each shall satisfy\\
When accounts are made\\
And none shall take us by surprise\\
For he hath fashioned them so,\\
Each in his day, each in its way.

One advised not to add to the work of God.\\
Add not to his works lest he rebuke thee\\
And thou be found wanting and a liar.\\
Where will the rebukes begin?\\
Will they start with Michael\\
For taking chances with Mammon\\
And giving life to Satan?

I know a pastor\\
Who keeps giving prophecies\\
And worshipping God.\\
When the devils struck out initially,

He gave a prophecy\\
And said God wanted me to live\\
And not get self-destructive.\\
He called me by name

And my neighbours,\\
The students nearby in my hostel\\
Started to play a notable song with my name;\\
I was cautious around them\\
And I was grieved at what they did to me.

Do not deceive yourselves\\
And say that we never understood your pain\\
And never saw that you were afflicted.\\
What if God does come and save me\\
And it is your turn to be harassed?\\
I too will give you words of encouragement\\
And not visit you even once or seek your welfare.

I will be like the accursed prophets\\
And pastors and shepherds\\
Whom James, disgusted at, rebuked,\\
The kind that are not deserving of heaven.

They serve God and worship\\
And give prophecies\\
But have no natural love.\\
They do not know what love is\\
Though they are married and I am not.

Maybe, a little pain will save them.\\
Maybe, they should be in my shoes\\
And listen to another pastor\\
Put himself in the shoes and place of God,\\
A pastor who prophesies a ring\\
And money, lots of wealth

And puts up a radiant image\\
With rays scattering in all directions\\
To demonstrate his brilliance.\\
Thou shalt surely be bright;\\
I do not doubt it.\\
Thou shalt shine for heaven to see

But learn compassion\\
And goodness and be kind.\\
I have found Christians\\
To be too heartless and cold.\\
I will die the day I go to church\\
On my own accord.

My words are ended.

What shall we end with?\\
Fear God and do good\\
And he shall bring forth thy light as the day.\\
Fear God and depart from evil.

It shall be light to thy soul\\
And vitality to thy bones.\\
Thou shalt have understanding\\
When you pursue the right path.

\bibliography{book.bib,packages.bib}

\end{document}
